Bestrophin-4 relays Hes4 and interacts with Twist1 to suppress epithelial-to-mesenchymal transition in colorectal cancer cells

Version 1

Abstract

Abstract

Bestrophin isoform 4 (BEST4) is a newly identified subtype of the calcium-activated chloride channel family. Analysis of colonic epithelial cell diversity by single cell RNA-sequencing has revealed the existence of a cluster of BEST4+ mature colonocytes in humans. However, if the role of BEST4 is involved in regulating tumour progression remains largely unknown. In this study, we demonstrate that BEST4 overexpression attenuates cell proliferation, colony formation, and mobility in colorectal cancer (CRC) in vitro, and impedes the tumor growth and the liver metastasis in vivo. BEST4 is coexpressed with hairy/enhancer of split 4 (Hes4) in the nucleus of cells, and Hes4 signals BEST4 by interacting with the upstream region of the BEST4 promoter. BEST4 is epistatic to Hes4 and downregulates Twist1, thereby inhibiting epithelial-to-mesenchymal transition (EMT) in CRC. Conversely, knockout of BEST4 using CRISPR/Cas9 in CRC cells revitalises tumor growth and induces EMT. Furthermore, the low level of the BEST4 mRNA is correlated with advanced and the worse prognosis, suggesting that BEST4 functions as a tumor suppressor in CRC.

Introduction

Colorectal cancer (CRC) is a common tumour worldwide. A steady increase in the morbidity and mortality of CRC has been reported (Rawla et al., 2019). When diagnosed in advanced stages, epithelial-mesenchymal transition (EMT) may occur as CRC metastasize to distal organs (Pastushenko and Blanpain, 2019; Sunlin Yong, 2021; Yeung and Yang, 2017; Zhang et al., 2021). EMT is a reprogramming process in which epithelial E-cadherin and ZO-1 are suppressed, and mesenchymal N-cadherin and vimentin are induced, transcriptionally mediated by Twist and the Snail family (Dongre and Weinberg, 2019).

The inhibition of EMT in breast cancer and prostate cancer has been associated with calcium-activated chloride channels (CaCCs) (Porretti et al., 2018; Walia et al., 2012), leading to various evaluations of CaCCs as a potential for cancer therapy (Li et al., 2017; Miotto and Struhl, 2006; Qu et al., 2019; Sui et al., 2014). The bestrophin (BEST) chloride channel, which is a member of a recently identified gene family, encodes several integral membrane proteins expressed on the basolateral membranes of epithelial cells; they regulate CaCCs to maintain homeostasis (Marmorstein et al., 2009; Tsunenari et al., 2003). Although there are four human evolutionarily-related genes (BEST1–BEST4) (Miller et al., 2019; Tsunenari et al., 2003), variant 4 is expressed predominantly in the colon (Fagerberg et al., 2014), where it gates electrolyte transportation in human intestinal epithelial cells (Ito et al., 2013). However, the role of BEST4 in the development of CRC and the mechanism behind its regulation are currently unknown.

In a recent analysis based on single cell RNA-sequencing analysis, it was discovered that a group of mature colonocytes expresses BEST4 (Parikh et al., 2019), and the subset of this group coexists with hairy/enhancer of split 4 positive (Hes4+) cells (Parikh et al., 2019). Hes4 belongs to a family of seven Hes genes (Hes1–7) that encodes a transcription factor with a basic helix-loop-helix motif. It is known to play a critical role in determining the fate and differentiation of progenitor cells during the development of various organs. Inhibiting the Twist1 transcriptional factor has been shown to mediate commitment to the differentiation of human bone marrow stem cells, as reported by several studies (El Yakoubi et al., 2012; Murato and Hashimoto, 2009; Nichane et al., 2008; Cakouros et al., 2015). Given this information, it is tempting to speculate that BEST4 may be associated with Hes4 and Twist1 in regulating EMT during CRC progression.

The aims of the present study are to: (1) establish the role BEST4 in CRC growth in vitro and in vivo; (2) determine the underlying molecular mechanisms by which BEST4 interacts with Hes4 and Twist1, and regulates EMT; and (3) explore the correlation of BEST4 gene expression with prognosis of CRC.

Results

BEST4 inhibits CRC proliferation, clonogenesis, migration, and invasion in vitro

To evaluate the effect of BEST4 on tumour growth, we constructed BEST4-expressing HCT116 and Caco2 CRC cell lines (Figure 1-supplemental figure 1A-1C) and showed that BEST4 overexpression halved cell proliferating rates of their respective empty vector (EV) controls when they were monitored in live and analysed using InCucyte (Figures 1A and 1B). This was accompanied by decreased cell viability (Figure 1-supplemental figure 1D and 1E). To determine the causal role of BEST4 in CRC tumorigenesis, we knocked out the BEST4 gene in HCT-15 using a CRISPR/Cas9 system (Figure 1- supplemental figure 1F-H). Consequently, there was a 50% increase in proliferation rates and viability compared with the parental control (Figures 1C and 1D; Figure 1-supplemental figure 1I). Rescued expression of BEST4 was able to reverse the observed effects on HCT-15 (Figure 1D; Figure 1- supplemental figure 1I).

BEST4 inhibits CRC cell proliferation, clonogenesis, migration, and invasion in vitro. Overexpression of BEST4 decreased proliferation of HCT 116 (A) and Caco2 (B) cells as determined by the IncuCyte confluence assay. (C) Viability of three individual BEST4-deleted clones as determined by a CCK-8 assay. (D) BEST4 deletion significantly enhanced cell viability compared with cells transduced with EV-gRNA control; the reintroduction of BEST4 resulted in suppressed cell growth as determined by IncuCyte confluence analysis. (E) Expression of BEST4-HA in HCT116 and Caco2 cells resulted in more colonies than cells transduced with EV plasmids (left panel); colonies were counted and analysed as shown (right panel). (F) A colony formation assay was performed to evaluate the responses of HCT-15 cells following BEST4 deletion and reintroduction (left panel); cell colonies were counted and analysed as shown (right panel). (G) Heterologous expression of BEST4 in HCT116 cells suppressed invasion and migration (upper panel, scale bar, 200 μm); cells that passed through the membrane were counted and compared (lower panel). (H) BEST4 deletion in HCT-15 cells promoted invasion, whereas reintroduction of BEST4 expression resulted in the inhibition of HCT-15 cell invasion and migration (upper panel, scale bar, 200 μm). Cells that passed through the membrane were counted and compared (lower panel). Data shown are the result of at least three independent experiments, with the mean ± SEM; *P<0.05, **P<0.01 vs EV or WT.

In contrast to the controls, BEST4 overexpression decreased colony formations of HCT116 and Caco2 by 60% and 70%, respectively (Figure 1E). While BEST4 deletion increased the number of colonies by five-fold in HCT-15 (Figure 1F), the rescued expression counteracted its enhancement (Figure 1F).

Furthermore, overexpression of BEST4 in HCT116 inhibited transwell migration and invasion by 70% and 80%, respectively, compared to EV controls (Figure 1G). But BEST4 ablation in HCT-15 increased cell migration and invasion by two-fold and three-fold, respectively. These pro-tumor effects on HCT-15 were also reversible when BEST4 expression was rescued (Figure 1H).

Collectively, these findings suggest the tumour-suppressive role of BEST4 in CRC growth in vitro.

BEST4 deters EMT in CRC in vitro and in vivo

Because EMT initiation is a critical process in tumour progression (Acloque et al., 2009), we evaluated the effect of BEST4 on EMT using qPCR and found that BEST4 expression upregulated CDH1 and ZO-1 and downregulated vimentin and Twist1 in HCT116 compared with the control (p < 0.05) (Figures 2A). Conversely, knockout of BEST4 in HCT15 downregulated CDH1 and ZO-1 and upregulated vimentin and Twist1. Rescued expression of BEST4 in HCT-15 reversed these gene alterations (Figures 2B). Changes of these genes were consistent with their corresponding protein expression as analysed by immunoblotting (Figures 2C and 2D).

BEST4 deters EMT in CRC in vitro and in vivo. (A) Expression of mRNAs encoding EMT-related genes as determined by qPCR in HCT116 cells transfected with BEST4-HA or EV. (B) As determined by qPCR, the expression of mRNAs encoding EMT markers in BEST4-deleted and BEST4-restored HCT-15 cells. (C) Protein expression of EMT-related genes was evaluated by western blotting of lysates of HCT116 cells transfected with BEST4-HA or EV. (D) Western blotting determined the levels of immunoreactive EMT markers in BEST4-deleted and BEST4-restored HCT-15 cells. (E) Growth of xenograft tumours in BALB/c nude mice resulting from the injection of HCT116 cells stably-transduced with BEST4-HA was significantly diminished compared with those resulting from HCT116 cells transduced with EV alone (eight mice per group). (F) The histogram represents the mean weights of tumours isolated from the HCT116-BEST4-HA and HCT116-EV groups. (G) Tumours from the HCT116-BEST4-HA and HCT116-EV groups were sectioned and subjected to immunohistochemical staining to detect HA and human Ki67; scale bar=50 μm. (H) Mean percentage of Ki67-positive staining in each group. (I) Representative western blot documenting protein levels of EMT markers in individual HCT116-BEST4 and HCT116-EV xenograft tumours. (J) Each band’s mean pixel intensities were determined and normalized to mean β-actin pixel intensity. *P<0.05, **P<0.01. Data from at least three independent experiments are presented as the mean ± SEM. (K and J) Intrasplenical injections of HCT-15 cell lines with EV-gRNA control, BEST4-gRNA or BEST4-Rescued (n = 3 per group). After 28 days, the animals were sacrificed and numbers of metastatic nodules in the liver were counted, and the liver tissues were fixed for sectioning and H&E staining. Data are presented as the mean ± SEM. **P<0.01 vs EV-gRNA.

Next, we subcutaneously implanted BEST4-HA-expressing HCT116 and EV control cell lines into BALB/c nude mice and monitored tumour growth weekly. When they reached the maximum allowable volumes (day 32), the animals were culled, and tumours were harvested. Essentially, the sizes and weights of tumours in BEST4 overexpression group were only half of the EV control (Figures 2E and 2F), in conjunction with the similar magnitude reduction of Ki67+ cells as analyzed by immunohistochemistry (Figure 2G and 2H). Further analysis of the HCT116 tumour tissue lysates showed that BEST4 deterred EMT by upregulating E-cadherin and, downregulating vimentin and Twist1 (Figures 2I and 2J).

We also evaluated the inhibitory role of BEST4 in a model of CRC to the liver metastasis by intrasplenically injecting HCT-15 cell lines with BEST4 knockout (BEST4gRNA) or the wild-type control (gRNA) or the knockout with the rescue (BEST4-Rescued) into BALB/c nude mice. We observed that there were 2-fold greater of the liver metastatic nodules in the BEST4 deficient tumors than the control (Fig. 2K and 2L). Conversely, the reconstituted BEST4 expression had no visible metastatic nodules in the liver, and the pathological analysis of the tissue sections by H&E staining also confirmed no detectable metastatic loci in the tissue sections (Fig. 2K and 2L).

These findings indicate the role of BEST4 in suppressing CRC tumorigenic activities, through counteracting EMT induction in models of in vitro and in vivo.

Hes4 upstream regulation of BEST4

Given the co-expression of BEST4+ and Hes4+ in a human colonic epithelial lineage (Parikh et al., 2019), we sought to investigate their biological interactions during tumour growth. Upon transfecting the Flag-Hes4 plasmid DNA into HCT116, we observed a responsive upregulation of both endogenous BEST4 mRNA and protein levels compared to the control transfectant (Figure 3A; Figure 3- supplemental figure 1A). This intrinsic association was further supported by knocking down the endogenous Hes4 with two pairs of shRNAs in LST174 that resulted in downregulation of endogenous BEST4 (Figure 3B; Figure 3-supplemental figure 1B).

Molecular regulation of BEST4 expression by Hes4. (A) Endogenous BEST4 mRNA and protein levels in Hes4-overexpressing HCT116 cells were detected by qPCR and western blotting, respectively. (B) Endogenous BEST4 mRNA and protein levels in LS174T cells after shRNA-mediated Hes4 knockdown as detected by qPCR and western blotting, respectively. (C) Detection of BEST4 promoter activity in Hes4-overexpressing HCT116 cells using a dual-luciferase reporter assay. (D) As determined by ChIP-qPCR, Fold-enrichment of the BEST4 promoter region in Flag-ChIP samples from Hes4-overexpressing HCT116 cells. Data were normalized using a fold-enrichment method (i.e., ChIP signals divided by control IgG signals). The DHFR 5’ UTR was used as a negative control (upper panel). The primer sets that target the BEST4 promoter in the ChIP-qPCR assays are as illustrated; +1 marks the transcriptional start site of BEST4, and P1, P2, P3, and P4 represent primer locations (lower panels). (E) Immunofluorescence staining documents the colocalization of BEST4 (green) and Hes4 (red) in HCT116 cells based on detection of their specific tags; scale bar, 20 μM. (F) Co-immunoprecipitation of nuclear extracts with specifically-tagged BEST4 and Hes4 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (G) Detection of BEST4 promoter activity in Hes4-overexpressing HCT116 cells after BEST4 knockdown through a dual-luciferase reporter assay. Data shown are the result of at least three independent experiments, with the mean ± SEM; *P<0.05, **P<0.01 vs EV

To explore how Hes4 regulates BEST4 expression at the transcriptional level, we transfected a BEST4 promoter-driven luciferase DNA construct into Hes4-expressing HCT116 and assessed the promoter activity using a dual-luciferase assay. Our results showed a four-fold increase in the promoter activity compared to the EV control (Figure 3C), Furthermore, ChIP-qPCR analysis using a Flag antibody to IP for Hes4 revealed a twelve-fold enrichment of the P3 region upstream of the BEST4 transcriptional start site compared to the control (Figure 3D). Interestingly, BEST4 overexpression in HCT116 cells did not affect Hes4 mRNA expression as quantified by qPCR (Figure 3-supplemental figure 1C), suggesting that Hes4 regulates BEST4 expression upstream. This speculation is supported by immunofluorescence staining, where we observed nuclear co-localization of BEST4 (green) and Hes4 (red) in HCT116 cells co-transfected with BEST4-HA and Flag-Hes4 plasmid DNAs, along with additional cytoplasmic expression of BEST4 (Figure 3E).

To evaluate the association of BEST4 with Hes4 at the translational level, we co-transfected their HA-tagged BEST4 and Flag-Hes4 plasmid DNAs into HEK293 cells, along with the respective single transfectant control. By conducting IP with antibodies specific to Flag or HA, we showed that BEST4 and Hes4 were reciprocally copurified from the nuclear protein lysates, but not with IgG controls (Figure 3F).

Collectively, these findings indicate that BEST4 interacts with Hes4 at both transcriptional and translational levels.

BEST4 relays Hes4 signal and directly downregulates Twist1 leading to EMT inhibition independent of the channel function in CRC

Because a step of Hes4 in committing to human bone marrow stromal/stem cell lineage-specific development is mediated by Twist1 downregulation (Cakouros et al., 2015), with evidence of direct interaction between BEST4 and Hes4 observed in HCT116, it is plausible that they could exploit Twist1 to regulate EMT. To test this notion, we transfected a Twist1 promoter-driven luciferase DNA construct into HCT116. In comparison with the EV control, Flag-Hes4 or BEST4-HA transfectants significantly decreased Twist1 promoter activity by almost half, as evaluated by the dual-luciferase assay (Figure 4A). Essentially, the BEST4 transfectant enhanced inhibition of the Twist promoter by 70% in Hes4-expressing HCT116 (Figure 4B), hence suggesting that BEST4 mediates the inhibition of the Twist1 promoter activity by Hes4. This effect was also observed when endogenous Hes4 was knocked down using shRNAs in HCT116 cells transfected with BEST4-HA plasmid DNA (Figure 4C).

BEST4 relays the Hes4 signal and directly downregulates Twist1 expression to counteract EMT induction in CRC (A) Detection of Twist1 promoter activity in Hes4-overexpressing or BEST4-overexpressing HCT116 cells through a dual-luciferase reporter assay. (B) Detection of Twist1 promoter activity in Hes4-overexpressing HCT116 cells after BEST4 knockdown through a dual-luciferase reporter assay. (C) Detection of Twist1 promoter activity in HCT116 cells after shRNA-mediated Hes4 knockdown and combination with BEST4-overexpressing using a dual-luciferase reporter assay. (D) Co-immunoprecipitation of nuclear extracts with specifically-tagged BEST4 and Twist1 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (E) Co-immunoprecipitation of nuclear extracts with specifically-tagged Hes4 and Twist1 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (F) Expression of EMT markers in Hes4-overexpressing HCT116 cells. (G) Expression of EMT markers in LS174T cells after shRNA-mediated Hes4 knockdown. (H) Expression of EMT markers in Hes4-overexpressing HCT116 cells after BEST4 knockdown. (I) Expression levels of EMT markers in BEST4-overexpressing LS174T cells after Hes4-knockdown; SCR, scrambled siRNA.

The association of BEST4 with the Twist1 promoter activity was also evidenced by their nuclear colocalization after transfecting BEST4-HA and Myc-Twist1 plasmid DNAs into HCT116 (Figure 4- supplemental figure 1A). Co-IP with antibodies to Myc or HA showed that they were copurified from the nuclear protein lysates, but not with the IgG controls from the transfectant cell lysates (Figure 4D: Figure 4-supplemental figure 1A). Additionally, the knockdown of endogenous BEST4 in Hes4-expressing HCT116 cells substantially decreased Flag-Hes4 coprecipitation from the nuclear protein lysates, while Myc-Twist1 expression remained constant, as determined by co-IP with antibodies to Flag or My (Figure 4E: Figure 4-supplemental figure 1B).

We then investigated the impact of Hes4 expression on EMT induction by overexpressing Hes4 in HCT116 cells. Our results showed there were upregulation of ZO-1 and E-cadherin epithelial molecules, and downregulation of Twist1 protein (Figure 4F) and the vimentin mRNA (Figure 4-supplemental figure 1C). The vimentin protein appeared to be undetectable in HCT116, which was consistent with a previous report (Roger et al., 2010). Nevertheless, knocking down endogenous Hes4 in LS174T cells using shRNAs targeting two Hes4 domains caused the opposite effect (Figure 4G).

To determine if BEST4 is downstream signal that relays Hes4 to regulate Twist1 expression and consequently EMT induction, we knocked down endogenous BEST4 with siRNAs in Hes4-expressing HCT116 and showed the corresponding downregulation of E-cadherin and ZO-1, with upregulation of Twist1 protein and the vimentin mRNA, as analyzed by immunoblotting and qPCR (Figure 4H; Figure 4-supplemental figure 1D). The opposite was true when BEST4 was overexpressed in LS174T (Figure 4I). Therefore, these findings infer BEST4-mediated upstream Hes4 to directly downregulate Twist1 and subsequently deter EMT in CRC.

Given the physiological role of BEST4 plays in regulating chloride/calcium flux, we evaluated the channel functional effect on EMT induction. After respectively incubating BEST4-expresing HCT116 and the EV control with 300μM DIDS (a broad blocker of chloride channel), or a gradient increase in doses of CaCCinh-A01 (a specific inhibitor of native calcium-activated chloride channels), or 1μM ionomycin (a calcium ionophore to activate the chloride channel) as published previously (Liu et al, 2015; Uwada et al, 2019), we showed that BEST4 significantly increased chloride/calcium fluxes and activated their exchanges and the expected inhibition by DIDS, CaCCinh-A01 or ionomycin (Fig. 4- supplementary figure 5A-5C). Through immunoblotting analysis, we recapitulated that BEST4 simultaneously upregulated both ZO-1 and E-cadherin, and downregulated Twist1. Essentially, the levels of these proteins remained constantly expressed when the cells were treated with DIDS or CaCCinh-A01 or ionomycin, respectively (Fig. 4-supplementary figure 5D-5F). Hence, these results suggest BEST4 protein-mediated EMT suppression is independent of its channel function in HCT116.

Correlation of the BEST4 gene with clinicopathology and outcomes of patients diagnosed with CRC

We showed evidence of the endogenous BEST4 mRNA and protein expression in HCT116 and LS174T CRC cell lines (Figures 3A and 3B); these findings prompted us to explore the potential clinically significant BEST4 expression in CRC. Initially with high-throughput whole transcriptome sequencing analysis of five pairs of CRCs and adjacent normal tissues (ANTs), we identified several significantly downregulated genes in CRC compared to ANTs; BEST4 was in the top four (Figures 5A and 5B). Further validation by qPCR in the paired tissues of 50 colorectal adenomas and 124 CRC showed that the BEST4 gene was expressed significantly less in adenomas and tumours than in ANTs (Figures 5C and 5D). Immunoblotting analysis of tissue lysates from five paired randomly selected samples showed that BEST4 protein was downregulated in CRC (Figures 5E). Using public datasets of The Cancer Genome Atlas (TCGA) and the Genotype-Tissue Expression (GTEx), we measured BEST4 gene expression in CRC and matched normal tissues with the online Gene Expression Profiling Interactive Analysis (GEPIA) tool (http://gepia.cancer-pku.cn/). As shown in Figure 6-supplemental figure 1A, the normal colorectal control tissues consistently expressed higher BEST4 than the CRC.

Correlation of the BEST4 gene with clinicopathology and outcomes of patients diagnosed with CRC. (A) Heatmap based on the top 100 differentially expressed genes (downregulated and upregulated) in CRCs compared with ANTs. (B) Volcano plots of RNA seq results showing all differentially expressed genes in CRC tissues compared with ANTs based on the fold-change (|FC|≥ 1) and P-value (P≤0.05). (C) Expression levels of BEST4 mRNA in 50 pairs of adenoma tissues compared with ANTs. (D) Expression levels of BEST4 mRNA in 124 pairs of CRC tissues compared with ANTs. (E) BEST4 protein levels in CRC and their matched counterparts were measured using western blotting. (F) Kaplan-Meier survival analysis according to BEST4 expression in 124 patients with CRC. The difference was statistically significant based on the log-rank test (P<0.01). (G) A working model delineates the mechanism by which BEST4 is transcriptionally activated by Hes4 and suppressed EMT through Twist1 inhibition: a. the expression of BEST4 is regulated by interactions of its upstream promoter region with Hes4. BEST4 positively promotes the transcriptional activity of Hes4 on BEST4 by physically binding to Hes4 in a positive feedback loop; b. The complex formed by BEST4 and Hes4 interacts with Twist1 and inhibits the promoter activity of Twist1. Hes4 alone is insufficient to inhibit Twist1 promoter activity, and BEST4 is required. Inhibition of Twist1 promoter activity by Hes4 is BEST4-dependent c. The complex formed by BEST4 and Hes4 destabilized Twist1; the same effect caused by Hes4 required BEST4 intermediation. The Hes4-BEST4-Twist1 axis counteracts EMT induction. *P<0.05, **P<0.01; CRC, colorectal cancer; ANT, adjacent normal tissue; T, tumour.

We further evaluated the clinicopathological significance of BEST4 expression in CRC patients by examining its correlation with gender, tumour-node-metastases stage, and lymph node metastasis based on the eighth edition of the American Joint Committee on Cancer Staging Manual (M. B. Amin et al., Springer, 2017). Interestingly, BEST4 expression in males was twice as high as in females (p=0.022, Table 1). Accordingly, high BEST4 gene expression correlated with more advanced stages (p=0.02, Table 1) and lymph node metastasis (between 0 and 2) (p=0.032, Table 1). Patients with high BEST4 expression had better overall survival than those with low expression (p<0.01, Figure 5F), which was confirmed by univariate survival analysis showing a lower risk of death (p<0.001, Table 2). Multivariate Cox regression analysis indicated that low levels of BEST4 mRNA were associated with poor prognosis of CRC patients (Hazard Ratio [HR], 0.285; 95% confidence interval, 0.157–0.606; P<0.001; Table 2).

After the significant reduction of the Hes4 gene through RNA sequencing analysis of our CRC patients (Figure 6-supplemental figure 1B and 1C), we proceeded to investigate the connection between BEST4 and Hes4 genes in TCGA and GTEx (http://gepia.cancer-pku.cn/). Our findings revealed a positive correlation between these genes (R = 0.47, p<0.001) (Figure 6-supplemental figure 1D), providing further evidence of their association in CRC. Furthermore, we conducted additional mining of TCGA or GTEx datasets using the GEPIA tool (http://gepia.cancer-pku.cn/) and observed a positive correlation between BEST4 and the CDH1 mRNA (R = 0.77, p<0.001), with a negative correlation with vimentin (R =–0.49, p<0.001) and Twist mRNA (R =–0.39, p<0.001)) (Figure 6-supplemental figure 1E-G). These correlation analyses of RNA sequencing data from our patients and publicly available datasets underscore the association of low BEST4 expression with worse outcomes in malignant CRC.

Discussion

In cancer cell cultures and mouse tumour xenografts, the present study shows that BEST4 inhibits the development of CRC. An axis comprising Hes4/BEST4/Twist1 governs the induction of EMT in CRC. BEST4 interacts with Hes4 at the transcriptional and translational levels, and directly downregulates Twist1 expression, resulting in EMT inhibition but independent of its channel functions. Our findings support the notion in several ways: (1) Hes4 binds to the promoter region of BEST4; (2) BEST4 colocalizes with Hes4 and Twist1 in the nucleus of cells, and protein-protein interactions; (3) the BEST4 inhibitory role in EMT exhibits upregulation of epithelial ZO-1 and E-cadherin, and downregulation of mesenchymal vimentin and Twist1 in CRC; and finally (4) low BEST4 mRNA levels were significantly correlated with malignant lesions and worse outcomes of CRC patients. To the best of our knowledge, this is the first characterization of the role of BEST4 in suppressing CRC progression and the underlying molecular mechanisms.

CaCCs are expressed widely in several types of epithelial and endothelial cells and are classified as calcium-dependent chloride channels (e.g., anoctamin-1 [ANO1 or TMEM16]), chloride channel accessory proteins (CLCAs), and members of the BEST family. The latter is a recent addition to the class of molecularly defined chloride channels (Huang et al., 2012). Calcium-dependent chloride channels and CLCAs are differentially expressed in CRC and normal colon tissues, exerting pro- or anti-growth effects, while little is known of BEST family in CRC (Li et al., 2017; Sanders et al., 2012; Sui et al., 2014; Yang et al., 2015). There are four subtypes of the BEST family in mammals that assemble as pentamers to form Ca2+-activated Cl- channels and maintain cellular physiological functions (Marmorstein et al., 2009; Milenkovic et al., 2008; Tsunenari et al., 2003). Subtypes of BEST1-3 are responsible for vitelliform macular dystrophy, regulating the cilia of olfactory sensory neuronal activity; others regulate cGMP-dependent calcium-activated chloride conductance in vascular smooth muscle cells (Matchkov et al., 2008; Pifferi et al., 2009). An intrinsic function of the BEST4 gene in modulating CRC growth remains poorly illustrated. In the present study, we demonstrated that BEST4 functionally inhibits the development of CRC in vitro and in vivo. BEST4 is transcriptionally regulated and physically interacts with upstream Hes4, leading to downregulation of Twist1 and EMT suppression. This suppression is independent of physiological Ca2+-activated Cl- channels since inhibition of BEST4-associated Ca2+- and Cl- fluxes did not alter ZO-1/E-Cadherin and Twist1 protein expression.

The recent identification of a heterogeneous BEST4+ and Hes4+ subgroup in a human colonic epithelial lineage (Parikh et al., 2019) led us to consider their potential role in regulating CRC progression. Among the Hes family, which is associated with intestinal progenitor cells in adenoma transformation, Hes1 and Hes4 are a paralog pair, with other members more distantly related (Katoh and Katoh, 2004). While Hes1 has been reported to induce EMT and promote metastasis and chemoresistance in CRC (Sun et al., 2017; van Es et al., 2005; Yuan et al., 2015), Hes4 is identified by our present study capable of combating EMT induction in a BEST4-dependent manner that is regulated at both transcriptional and translational levels.

The Twist1 transcriptional factor plays a crucial role in inducing EMT, which contributes to the malignant lesions (Yang et al., 2004). Its physical interaction with Hes4 determines human bone marrow stromal/stem cell differentiation (Cakouros et al., 2015). Twist1, a basic helix-loop-helix transcription factor, represses the expression of E-cadherin and ZO-1 and induces several mesenchymal markers including vimentin, which is a pivotal predictor of CRC progression (Nagai et al., 2016; Yang et al., 2004; Bulzico et al., 2019; Meng et al., 2018; Nagai et al., 2016; Yang et al., 2004; Vesuna et al., 2008; Yang et al., 2004; Yusup et al., 2017; Zhu et al., 2015). Despite Twist1 importance in CRC, little is known about how it is controlled during EMT induction. Our present study reveals that Twist1 colocalized and interacted with BEST4 in the nucleus of CRC HCT116 cells, leading to downregulation of Twist1 and inhibition of EMT. Hes4 also caused the same effect, but through intermediation with BEST4. Although the mechanistic insights of their interplay remain to be elucidated, the present study identifies the Hes4-BEST4-Twist1 axis that contributes to counter EMT in the development of CRC (Figure 5G).

Lastly, our analysis of correlations reveals the clinical significance of BEST4 expression in CRC. In particular, the mRNA levels of BEST4 were lower in tissues of both precancerous adenomatous lesions and CRC than ANTs. These alterations are significantly correlated with large tumour size, positive nodes, and poor overall survival, especially in male patients. Interestingly, a previous study conducted on a Chinese cohort reported an approximately 40% higher incidence of CRC in males than in females (Zhang et al., 2019). But it remains to be investigated whether sex hormone-related factors plays a role in the gender-specific downregulation of BEST4 and its impact on CRC in males (Yu et al., 2020).

In conclusion, the functional significance of BEST4 in CRC development and its interplay with other molecules is completely unknown. The present study demonstrates the role of BEST4 in inhibiting CRC proliferation, migration, and invasion both in models of in vitro and in vivo. Mechanically, BEST4 is epistatic to Hes4 for downregulating Twist1 and inhibits EMT in CRC. Therefore, we reveals a previously unknown mechanism of the Hes4-BEST4-Twist axis that restrains the progression of CRC.

Materials and Method

Clinical samples

A total of 124 samples of paired CRC and adjacent normal tissue and 50 samples of paired adenoma and ANT were collected randomly from clinical specimens from patients undergoing intestinal resections or upper gastrointestinal endoscopies at the Department of Gastrointestinal Surgery and Digestive Endoscopy Centre, West China Hospital, China, between January and December 2013. All patients were followed until December 2018 or until death. Samples from patients with malignant tumours in other organs, from patients who received preoperative chemotherapy or radiotherapy, and from patients with incomplete follow-up data were excluded. The survival time was calculated from the surgery date to the follow-up deadline (above) or until the date of death. The Ethics Committee of West China Hospital, Sichuan University (Sichuan, China) approved the study. All procedures were performed per the 1964 Declaration of Helsinki. Written informed consent was obtained from all participants.

Cell cultures and reagents

The human colon cancer cell lines Caco-2, HCT116, HCT-15, and LS174T were purchased from The American Type Culture Collection (Manassas, VA, USA). Cells were authenticated using short tandem repeat analysis performed within two years of receipt. Cells at passages >15 were not used. All cells were maintained in Dulbecco’s Modified Eagle’s medium (DMEM; Gibco, Waltham, MA, USA) supplemented with 10% foetal bovine serum (FBS), 100 U/mL penicillin, and 100 mg/mL streptomycin. Before each experiment, cells were provided with low glucose (1 g/L) DMEM with 5% FBS before adding experimental reagents. All cell lines were frequently examined using the MycoAlertTM Mycoplasma Detection Kit (Lonza, Verviers, Belgium) to ensure they remained free of mycoplasma contamination.

Tumour and CRC hepatic metastasis mouse xenografts

Four-week-old female BALB/c nude mice were housed under standard conditions. The mice were randomized into two groups, with eight mice per group. HCT116 cells (5×106 cells in 0.1 mL phosphate-buffered saline) transduced with the lentivirus containing BEST4 or EV were injected subcutaneously into the right dorsal flank of mice. Tumour growth was measured twice a week using callipers, and tumour volumes were calculated as length x width2 x 0.5. Mice were sacrificed at 32 days, and tumour weight was measured at the end of the experiment. For further analysis, the excised tumour tissues were divided into two parts and embedded in paraffin or preserved at −80 °C for further analysis.

For the liver metastasis of CRC, intrasplenic injections of HCT-15 cells with BEST4-knockout (BEST4-gRNA), BEST4-rescued or control (EV-gRNA) (5×106 cells in 0.1 mL PBS) were performed into 6-week-old Balb/c nude mice as described previously2. There were 3 mice/group. Briefly, at day 28 after the procedure, mouse livers were paraffin embedded and the sections for H&E staining. The numbers of the metastatic nodules on the livers were double-blind visually quantified and confirmed by a pathologist.

The Animal Ethics Committee approved animal experiments of West China Hospital, Sichuan University (Sichuan, China).

CRC cell lines with overexpression of BEST4

Forced overexpression of BEST4 was examined in HCT116 and Caco2 CRC cells in which the C-terminal HA epitope-tagged human BEST4 gene with GFP (BEST4-HA-GFP) or GFP alone was introduced by lentivirus-mediated gene transfer. Fluorescence-activated cell sorting (FACS) was performed to obtain single cells distributed into 96-well plates. Three independent lines with the highest levels of BEST4 expression were used for subsequent experiments (Figures S1A and S1B). BEST4 mRNA and HA-tagged protein levels were significantly higher in HCT116 and Caco2 cells transfected with BEST4-HA plasmids than those transfected with the empty vector (EV) alone (Figure S1C). The BEST4-overexpressing cell lines were named “HCT116 BEST4-HA” and “Caco2 BEST4-HA.” Cells transfected with the EV alone were referred to as “HCT116 EV” and “Caco2 EV.”

CRISPR/Cas9-mediated knockout of BEST4

BEST4-depleted HCT-15 cells were generated with CRISPR/Cas9 gene-editing technology using a dual sgRNA approach. Two sequences that targeted exon 3 within the BEST4 active fragment (5’- TGACTCTCGTGGTGAACCGC-3’ and 5’-CCGAGATGACGCACATCAGC -3’) were inserted into the pU6-gRNA-Cas9-EGFP vector (GenePharma, Shanghai, China) to generate a CRISPR/Cas9 BEST4 knockout plasmid. Excision of the targeted 44 bp genomic fragment resulted in splicing errors in exons 2 to 4 and generated a premature STOP codon that abrogated functional gene expression (Figures S1F and S1G). Cells were transfected with these plasmids, and GFP+ cells were FACS-sorted as single cells into 96-well plates. After culturing for three weeks, cells were distributed into two 24-well plates, and the appropriate deletion was verified by sequencing. Only cell lines with homozygous deletions were used. Three independent lines generated using this method were used for subsequent experiments and were named “HCT15 BEST4-gRNA.” Diminished expression of immunoreactive BEST4 protein was confirmed by immunoblotting (Figure S1H). The same overexpression strategy was adopted to rescue BEST4 expression in BEST4 knockout HCT-15 cells, named “HCT15 BEST4-Rescued.”

Plasmids and transfection/transduction

Expression plasmids encoding BEST4 (GeneID: 266675, NM_153274; vector: pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro) containing a C-terminal hemagglutinin (HA) epitope tag, HES4 (GeneID: 57801, NM_001142467.2; vector: pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro) containing a N-terminal Flag epitope tag,were synthesized by Public Protein/Plasmid Library (Nanjing, China). According to the manufacturer’s instructions, Lipofectamine 3000 (Invitrogen, Carlsbad, CA, USA) was used in cell transfection experiments.

To generate a model of CRC with forced overexpression of Hes4, cells were transfected with lentiviral pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro vectors containing human Hes4 cDNA and selected with puromycin (Invivogen, San Diego, CA, USA) at 10 µg/mL introduced 48 h after transfection.

For short hairpin RNA (shRNA) and RNA silencing (siRNA) experiments, HEK293 cells were co-transduced with lentiviral vectors carrying shRNA targeting HES4 (Public Protein/Plasmid Library, Nanjing, China; target sequences are listed in Table S1). Supernatants were collected at 48 and 72 h for analysis. Scrambled shRNAs were used to control for non-specific effects. Transduction was performed by mixing aliquots of lentivirus with a standard medium containing 10 μg/mL puromycin (Invivogen) to remove untransduced cells. GeneSolution siRNAs targeting BEST4 (BEST4-siRNA) were used to silence gene expression. Scrambled siRNA (SCR) was used as a control (Qiagen, Hilden, Germany). The target sequences of the BEST4 siRNAs are listed in Table S1. For siRNA experiments, cells were seeded one day before transfection in an antibiotic-free medium and grown to 60% confluency in six-well plates. Cells were transfected using Lipofectamine 3000 as per the manufacturer’s protocol. The efficiency of RNA interference was determined using quantitative polymerase chain reaction (qPCR) and western blotting.

RNA isolation, cDNA library preparation, sequencing, and data analysis

Total RNA was isolated using a High Pure RNA Isolation Kit (Roche, Basel, Switzerland). RNA samples with an RNA integrity number (RIN) ≥7.0 and a 28S:18S ratio ≥ 1.5 were used in subsequent experiments. Sequencing libraries were generated and sequenced by CapitalBio Technology (Beijing, China). A total amount of 3 μg RNA per sample was used. Briefly, the Ribo-Zero™ Magnetic Kit (Epicentre) was used to remove rRNA from the total RNA, and then the NEBNext Ultra RNA Library Prep Kit for Illumina (NEB, USA) was used to construct the libraries for sequencing following the manufacturer’s instructions. The RNA was fragmented into pieces of ∼200 base pairs in length in NEBNext First-Strand Synthesis Reaction Buffer (5X). The first-strand cDNA was synthesized from the RNA fragments using reverse transcriptase and random hexamer primers, and then the second-strand cDNA was synthesized in Second-Strand Synthesis Reaction Buffer with dUTP Mix (10x). The end of the cDNA fragment was subjected to an end-repair process that included the addition of a single “A” base followed by ligation of the adapters. Products were purified and enriched using PCR to amplify the library DNA. The final libraries were qualified using Agilent 2100 and quantified using the KAPA Library Quantification Kit (KAPA Biosystems, South Africa). Finally, the libraries were subjected to paired-end sequencing with a paired-end 150-base pair reading length on an Illumina NovaSeq sequencer (Illumina).

The sequencing quality of raw data in fastq format was assessed using FastQC, and then low-quality data were filtered using the Next Generation Sequencing Quality Control platform. The high-quality clean reads were then aligned to the reference genome using Tophat2 with default parameters. The genome of the human genome version of hg38 (UCSC) was used as the reference. Cufflinks and Cuffmerge software packages were used to assemble the transcripts. All subsequent comparative analyses of lncRNAs and mRNAs were based on the results of the transcripts. Transcripts corresponding to mRNAs or lncRNAs were collected from databases and treated as known lncRNAs and annotated based on information from public databases. The transcripts were treated as novel lncRNAs when their sequence length was >200 and when they were predicted to be non-coding RNAs. Differential expression analyses were performed using the limma package and edgeR. Functional annotation and enrichment analyses were performed using KOBAS 3.0. The target genes of the mRNAs were predicted based on cis- and trans-patterns based on the location on the reference genome and sequence similarity. The raw sequence data reported in this paper were deposited in the NCBI Sequence Read Archive with accession number PRJNA690126.

RNA extraction and real-time PCR

Total RNA was isolated from cell lysates according to the manufacturer’s protocol (Zymo Research, Tustin, CA). A High-Capacity cDNA Reverse Transcription Kit (Thermo Fisher Scientific, Waltham, MA) was used for first-strand cDNA synthesis with 1 µg of total RNA from each sample. The expression of genes and the GAPDH internal control was assayed by qPCR using SYBR Green (Bioline Reagents Ltd, London, UK). Primer sequences are shown in Table S1.

Immunoblotting

Protein extracts were prepared using RIPA lysis buffer (Merck Millipore, Temecula, CA) containing protease inhibitor cocktail and phosphatase inhibitor tablets (Sigma, MO, USA). Protein content was determined using a protein assay kit (Bio-Rad, Hercules, CA). Western blotting was performed as described previously (Wang et al., 2019). All primary (1:1000) and secondary antibodies (1:2000), except BEST4 (1:800; LsBio, Seattle, WA) and anti-Flag M2 (Sigma, MO, USA), were purchased from Cell Signaling Technology (Danvers, MA, USA).

Cell proliferation

Cell proliferation was monitored in real time using an IncuCyte ZOOM live-cell microscope incubator (Essen Bioscience, MI, USA), in which the cell confluence was calculated using IncuCyte software, and the cell proliferation was expressed as the percentage of confluence. According to the manufacturer’s protocol, a Cell Counting Kit-8 (CCK-8, Dojindo, Tokyo, Japan) assay was used to confirm cell viability. The absorbance at 450 nm was measured using a microplate reader (BioTek, VT, USA), and growth curves were drawn according to the optical density.

Clonogenesis

A total of 3×103 cells per well were seeded in 6-well plates. The medium was refreshed twice a week. After 2 weeks, colonies were fixed and stained with crystal violet (0.005% in 20% methanol). The numbers of colonies were quantified using GelCount (Oxford Optronix Ltd, Oxford, UK). The assay was carried out in triplicate wells for three independent experiments.

Transwell migration and invasion

Cells were digested and suspended in culture medium without FBS for the migration assay. Cell suspensions were added into the upper chamber of the Transwell insert and then placed into the 24-well plate Transwell containing medium with 10% FBS in the lower chamber. For the invasion assay, the 24-well plate with Transwell inserts was coated with 50 μg/insert of Matrigel matrix on the top of the chamber (BD Biosciences, Oxford, UK). After 48 h, cells that travelled to the lower surface of the insert were stained with crystal violet. Experiments were conducted in triplicate.

Immunohistochemistry

Paraffin-embedded tissue blocks from formalin-fixed tumour samples were sectioned, dewaxed, and rehydrated following standard protocols. Sections were stained for human Ki67 primary antibody (1:200, Cell Signaling Technology, MA, USA), a marker of cell proliferation, and anti-mouse HRP-conjugated secondary antibody (Dako, CA, USA), and the positive cells were counted in eight randomly chosen fields. Expression of BEST4-HA in tumours was stained with anti-HA primary antibody (1:800, Cell Signaling Technology) and anti-rabbit HRP-conjugated secondary antibody (Dako).

Dual-luciferase reporter assay

The BEST4 promoter region (−2000 to +100 bp) was cloned into pGL3-basic vectors (Promega, WI, USA) to construct the luciferase reporter plasmid (pGL3-BEST4). The stably high Hes4 expression cell line was constructed by infecting HCT116 cells with lentivirus, and then the recombinant plasmid pGL3-BEST4 was co-transfected with the control plasmid pRL-TK (Promega) into HCT116 Hes4 and HCT116 EV cells. Twenty-four hours after transfection, firefly and Renilla luciferase activities were analysed using the dual-luciferase reporter assay (Promega) according to the manufacturer’s instructions, and the results were normalized as relative luciferase activity (firefly luciferase/Renilla luciferase).

Chromatin immunoprecipitation-quantitative PCR (ChIP-qPCR)

ChIP-qPCR was performed as previously described (Miotto and Struhl, 2006). At room temperature, we crosslinked cells at 5×107 cells/mL for 10 min using 1% formaldehyde and stopped the reaction using 125 mM glycine. After three washes with ice-cold PBS, cells were homogenized, lysed, and sonicated to shear DNA into 200–500 bp fragments. The DNA fragments were incubated with 10 µg of antibodies against anti-Flag tag (Sigma, MO, USA) or native IgG (Cell Signaling Technology) followed by IP with 60 µl of protein A/G Magnetic Beads (MedChemExpress, New Jersey, USA) and overnight incubation at 4 °C with rotation. Immunoprecipitated DNAs were extracted from the DNA/antibody/protein A/G bead complexes using proteinase K digestion, subjected to reverse crosslinking at 65 °C for 4 h, and purified with spin columns. qPCR analysis was performed to determine the enrichment of DNA fragments using the indicated primers (Table S1). ChIP-qPCR data were normalized using the fold-enrichment method (ChIP signals were divided by IgG signals), and DHFR 5 ’UTR was used as a negative control. Each experiment included triplicate samples and the data shown represent the mean of three independent experiments.

Immunofluorescence staining

HCT116 cells transfected alone or co-transfected with expression vectors encoding C-terminal HA-tagged BEST4, and N-terminal Flag-tagged Hes4 were grown on glass coverslips, fixed for 10 min with 4% paraformaldehyde, permeabilized for 5 min with 0.2% Triton X-100, then blocked for 15 min with 3% bovine serum albumin. HA-tagged BEST4 was stained using an anti-HA antibody (Cell Signaling Technology) followed by a TRITC-labelled secondary antibody (Abcam, Cambridge, UK). Flag-tagged Hes4 was detected using an anti-Flag antibody (Sigma, MO, USA) with an Alexa Fluor 647-labeled secondary antibody (Invitrogen Carlsbad, CA). Cells were mounted and imaged using laser-scanning confocal microscopy (Nikon Corporation, Tokyo, Japan).

Co-immunoprecipitation (Co-IP)

Co-IP assays were performed on nuclear extracts. According to the manufacturer’s protocols, nuclear proteins of each sample were collected using MinuteTM Cytoplasmic and Nuclear Fractionation Kit (Invent, MN, USA). Protein G Dynabeads (Thermo Fisher Scientific, MA, USA) following the manufacturer’s instructions. Briefly, HEK293 cells were co-transfected with expression vectors encoding C-terminal HA-tagged BEST4 and N-terminal Flag-tagged Hes4. Cells were harvested and lysed 48 h after transfection. Cell lysates (500 µg) were incubated overnight at 4 °C in a rotating wheel with 2 µg of anti-FLAG (Sigma, MO, USA) or anti-HA antibody (Cell Signaling Technology) bound to Protein G Dynabeads. Immunocomplexes were separated using a magnet, washed three times in PBS with 0.02% TweenTM 20 and eluted in elution buffer (50 mM glycine pH 2.8). After boiling in sample buffer at 70 °C for 10 min, immunocomplexes were loaded on 4–20% Tris-glycine gels (Bio-Rad, CA, USA), followed by blotting on PVDF membranes and immunoblotting using the indicated antibodies.

Chloride channel efflux

Cells were maintained in a serum free DMEM overnight prior to treatment with DIDS (4,4’- diisothiocyanatostilbene-2,2’-disulfonic acid; HY-D0086, MCE, China), CaCCinh-A01 (HY-100611, MCE, China) or 1 μM ionomycin for 24h as previously published (Liu et al, 2015; Uwada et al, 2019). Chloride channel efflux was evaluated with colorimetric changes by commercially available kits (ab176767, Abcam). Briefly, 40,000 BEST4-expressing or EV-control HCT116 cells were plated per well in a 96-well plate and allowed to grow over night. Before the assay, cells were refreshed with serum-free medium and 100 µL/well of pre-warmed iodide-loading buffer was added and the plate was incubated for 2 hours at 37 ℃. After washing each well with HBSS three times, cells were lysed and Iodide Sensor Blue dye (50 µL/well) and 0.5 x Iodide Sensor Enhancer (50 µL/well) were added and incubated for 1 minutes before reading at 405 nm. Data was calculated as fold-change relative to control.

Statistical analysis

The results were expressed as the mean ± standard error of the mean. The statistical significance of differences between means was assessed using Student’s unpaired two-tailed t-tests, and the Mann-Whitney U test was performed to compare the variables in two groups using SPSS 25.0 (SPSS, Chicago, USA). The relationship between the clinicopathological parameters of CRC and the expression of BEST4 was examined using the Kruskal-Wallis H test. The Kaplan-Meier method and log-rank tests were used to assess overall survival in relation to BEST4 expression. Differences in cell proliferation and tumour growth rates between the two groups of mice were assessed using repeated-measures analysis of variance. Western blot intensity was assessed using ImageJ v1.53 software (ImageJ, Bethesda, MD, USA). P-values <0.05 indicated statistically significant differences.

Data and code availability

The raw sequence data reported in this paper have been deposited in the NCBI Sequence Read Archive (SRA) with accession number PRJNA690126.

Compliance and ethics

The author(s) declare that they have no conflict of interest. The clinical studies were approved by the Ethics Committee of West China Hospital, Sichuan University (Sichuan, China). All procedures were performed per the 1964 Declaration of Helsinki. Written informed consent was obtained from all participants. The Animal Ethics Committee approved animal experiments of West China Hospital, Sichuan University (Sichuan, China).

Supporting information

eLife Assessment

The findings of this valuable manuscript advance our understanding of the significance of Bestrophin isoform 4 (BEST4) in suppressing colorectal cancer (CRC) progression. The authors used appropriate and validated methodology, such as the knockout of BEST4 using CRISPR/Cas9 in CRC cells, to provide a solid foundation for elucidating the potential link between BEST4 and CRC progression.

Reviewer #1 (Public Review):

Summary:

In this study, the authors describe the participation of the Hes4-BEST4-Twist axis in controlling the process of epithelial-mesenchymal transition (EMT) and the advancement of colorectal cancers (CRC). They assert that this axis diminishes the EMT capabilities of CRC cells through a variety of molecular mechanisms. Additionally, they propose that reduced BEST4 expression within tumor cells might serve as an indicator of an adverse prognosis for individuals with CRC.

Strengths:

• Exploring the correlation between the Hes4-BEST4-Twist axis, EMT, and the advancement of CRC is a novel perspective and gives readers a fresh standpoint.

• The whole transcriptome sequence analysis (Figure 5) showing low expression of BEST4 in CRC samples will be of broad interest to cancer specialists as well as cell biologists although further corroborative data is essential to strengthen these findings (See Weaknesses).

Weaknesses:

• The authors employed three kinds of CRC cell lines, but not untransformed cells such as intestinal epithelial organoids which are commonly used in recent research.

• The authors use three different human CRC cell lines with a lack of consistency in the selection of them. Please clarify 1) how these lines are different from each other, 2) why they pick up one or two of them for each experiment. To be more convincing, at least two lines should be employed for each in vitro experiment.

• The authors demonstrated associations between BEST4 and cell proliferation/viability as well as migration/invasion, utilizing CRC cell lines, but it should be noted that these findings do not indicate a tumor-suppressive role of BEST4 as mentioned in line 120. Furthermore, while the authors propose that "BEST4 functions as a tumor suppressor in CRC" in line 50, there seems no supporting data to suggest BEST4 as a tumor suppressor gene.

• The HES4-BEST4-Twist1 axis likely plays a significant role in CRC progression via EMT but not CRC initiation. Some sentences could lead to a misunderstanding that the axis is important for CRC initiation.

• The authors mostly focus on the relationship of the HES4-BEST4-Twist1 axis with EMT, but their claims sometimes appear to deviate from this focus.

• Some experiments do not appear to have a direct relevance to their claims. For example, the analysis using the xenograft model in Figure 2E-J is not optimal for analyzing EMT. The authors should analyze metastatic or invasive properties of the transplanted tumors if they intend to provide some supporting evidence for their claims.

• In Figure 4H, ZO-1 and E-cad expression looks unchanged in the BEST4 KD.

• The in vivo and in vitro data supporting the whole transcriptome sequence analysis (Figure 5) is mostly insufficient. Including the following experiments will substantiate their claims: 1) BEST4 and HES4 immunostaining of human surgical tissue samples, 2) qPCR data of HES4, Twist1, Vimentin, etc. as shown in Figure 5C, 5D.

• Some statements are inconsistent probably due to grammatical errors. (For example, some High/low may be reversed in lines 234-244.)

Reviewer #2 (Public Review):

Summary:

Using in vitro and in vivo approaches, the authors first demonstrate that BEST4 inhibits intestinal tumor cell growth and reduces their metastatic potential, possibly via downstream regulation of TWIST1.

They further show that HES4 positively upregulates BEST4 expression, with direct interaction with BEST4 promoter region and protein. The authors further expand on this with results showing that negative regulation of TWIST1 by HES4 requires BEST4 protein, with BEST4 required for TWIST1 association with HES4. Reduction of BEST1 expression was shown in CRC tumor samples, with correlation of BEST4 mRNA levels with different clinicopathological factors such as sex, tumor stage, and lymph node metastasis, suggesting a tumor-suppressive role of BEST4 for intestinal cancer.

Strengths:

• Good quality western blot data.

• Multiple approaches were used to validate the findings.

• Logical experimental progression for readability.

• Human patient data / In vivo murine model / Multiple cell lines were used, which supports translatability / reproducibility of findings.

Weaknesses:

• Interpretation of figures and data (unsubstantiated conclusions).

• Figure quality.

• Figure legends lack information.

• Lacking/shallow discussion.

• Requires more information for reproducibility regarding materials and methods.

Author response:

The following is the authors’ response to the original reviews.

Public Reviews:

Reviewer #1 (Public Review):

Summary:

In this study, the authors describe the participation of the Hes4-BEST4-Twist axis in controlling the process of epithelial-mesenchymal transition (EMT) and the advancement of colorectal cancers (CRC). They assert that this axis diminishes the EMT capabilities of CRC cells through a variety of molecular mechanisms. Additionally, they propose that reduced BEST4 expression within tumor cells might serve as an indicator of an adverse prognosis for individuals with CRC.

Strengths:

• Exploring the correlation between the Hes4-BEST4-Twist axis, EMT, and the advancement of CRC is a novel perspective and gives readers a fresh standpoint.

• The whole transcriptome sequence analysis (Figure 5) showing low expression of BEST4 in CRC samples will be of broad interest to cancer specialists as well as cell biologists although further corroborative data is essential to strengthen these findings (See Weaknesses).

Weaknesses:

(1) The authors employed three kinds of CRC cell lines, but not untransformed cells such as intestinal epithelial organoids which are commonly used in recent research.

Sincerely thanks for catching this issue. While we acknowledge the potential of intestinal epithelial organoids as a valuable model for this study and will consider establishing this system in future research, which falls outside the scope of our current work.

(2) The authors use three different human CRC cell lines with a lack of consistency in the selection of them. Please clarify 1) how these lines are different from each other, 2) why they pick up one or two of them for each experiment. To be more convincing, at least two lines should be employed for each in vitro experiment.

We apologize for any confusion caused to the reviewer. In our study, we employed HCT116 and Caco2 cell lines to investigate the overexpression of BEST4 in the biological functions of CRC and its involvement in EMT. The selection of HCT116, a human CRC cell line, was based on its relatively lower expression level of BEST4 compared to other CRC cell lines. Conversely, Caco2 is a human colon adenocarcinoma cell line that closely resembles differentiated intestinal epithelial cells and exhibits microvilli structures. Given that BEST4 serves as a marker for intestinal epithelial cells, these two cell lines were chosen for investigating the in vitro effects of overexpressing BEST4 on proliferation, clonality, invasion, migration of colon cancer tumor cells and expression of downstream EMT-related markers. Similarly, we selected the HCT-15 cell line derived from human CRC for BEST4 knockout due to its comparatively higher expression level of BEST4 among other CRC cell lines. We employed the CRISPR/Cas9 gene-editing technology to knockout BEST4 instead of utilizing shRNA for downregulating BEST4 expression, thereby limiting our selection to a single cell line.

(3) The authors demonstrated associations between BEST4 and cell proliferation/ viability as well as migration/invasion, utilizing CRC cell lines, but it should be noted that these findings do not indicate a tumor-suppressive role of BEST4 as mentioned in line 120. Furthermore, while the authors propose that "BEST4 functions as a tumor suppressor in CRC" in line 50, there seems no supporting data to suggest BEST4 as a tumor suppressor gene.

We apologize for these inaccurate expressions, and we have made the necessary modifications to the corresponding parts in the manuscript.

(4) The HES4-BEST4-Twist1 axis likely plays a significant role in CRC progression via EMT but not CRC initiation. Some sentences could lead to a misunderstanding that the axis is important for CRC initiation.

We apologize for these inaccurate expressions, and we have made the necessary modifications to the corresponding parts in the manuscript.

(5) The authors mostly focus on the relationship of the HES4-BEST4-Twist1 axis with EMT, but their claims sometimes appear to deviate from this focus.

We apologize for confusing the reviewer. The objectives of our study are as follows: (1) to establish the role of BEST4 in CRC growth both in vitro and in vivo; (2) to determine the underlying molecular mechanisms by which BEST4 interacts with Hes4 and Twist1, thereby regulating EMT; and (3) to investigate the correlation between BEST4 expression and prognosis of CRC. We have made the necessary modifications to the corresponding parts in the manuscript.

(6) Some experiments do not appear to have a direct relevance to their claims. For example, the analysis using the xenograft model in Figure 2E-J is not optimal for analyzing EMT. The authors should analyze metastatic or invasive properties of the transplanted tumors if they intend to provide some supporting evidence for their claims.

Sincerely thanks for catching this issue. The process of EMT transforms epithelial cells exhibiting a spindle fibroblast-like morphology, leading to the acquisition of mesenchymal characteristics and morphology, enabling these cells to acquire invasive and migratory abilities, with expression switching epithelial E-cadherin and Zo-1 to mesenchymal vimentin (Dongre and Weinberg, 2019)..The whole process is regulated by transcriptional factors of the Snail family and Twist1(Dongre and Weinberg, 2019). We utilized the xenograft model with overexpressed BEST4 to analyze the lysates of tumor tissue, revealing that BEST4 upregulated E-cadherin and downregulated vimentin and Twist1 (Figures 2I). These findings indicate that BEST4 inhibits EMT in vivo. Deletion of BEST4 may enable these cells to acquire invasive and migratory abilities, leading to metastasis in vivo. Therefore, we subsequently evaluated the metastatic potential of BEST4 in a CRC liver metastasis model by intrasplenically injecting HCT-15 cell lines with knockout of BEST4 (BEST4gRNA), wild-type control (gRNA), or knockout with rescue (BEST4-Rescued) into BALB/c nude mice. Our observations revealed a twofold increase in liver metastatic nodules in the absence of BEST4 compared to the control group (Fig. 2J-L). Although further in vivo experiments are required for confirmation, our research suggests a potential role for BEST4 in counteracting EMT induction in vivo.

(7) In Figure 4H, ZO-1 and E-cad expression looks unchanged in the BEST4 KD.

Sincerely thanks for catching this issue. We have implemented the necessary modifications to the corresponding sections in the manuscript and performed a comprehensive quantification of all Western Blot data to ensure statistically significant differences, including those presented in the supplementary file.

(8) The in vivo and in vitro data supporting the whole transcriptome sequence analysis (Figure 5) is mostly insufficient. Including the following experiments will substantiate their claims: 1) BEST4 and HES4 immunostaining of human surgical tissue samples, 2) qPCR data of HES4, Twist1, Vimentin, etc. as shown in Figure 5C, 5D.

Sincerely thanks for catching this issue.

(1) Due to the substandard quality of the BEST4 antibody, we opted to evaluate the clinical significance of BEST4 in CRC by assessing mRNA results instead of protein levels using immunohistochemistry (IHC). After testing multiple antibodies for western blotting, only one (1:800; LsBio, LS-C31133) accurately indicated BEST4 protein expression while still exhibiting some non-specific bands. Consequently, we decided to transfect a HA-tagged BEST4 plasmid into the CRC cell line and used HA as a marker for BEST4 expression. Unfortunately, none of the antibodies employed for IHC were suitable as they failed to accurately distinguish between positive or negative staining for BEST4 and showed significant non-specific staining (data not shown). The challenge in detecting BEST4 protein in colorectal cancer tissues may be attributed to its low expression levels. Our findings are consistent with previous reports from the Human Protein Atlas database (https://www.proteinatlas.org/ENSG00000142959-BEST4/pathology), which also did not detect any BEST4 protein expression in colorectal cancer tissues through IHC analysis.

(2) The qPCR data of E-cadherin, Twist1, and Vimentin mRNA expression in CRC tissue has already been published in other studies(Christou et al., 2017; Lazarova and Bordonaro, 2016; Zhu et al., 2015). It was found that E-cadherin is downregulated, while Twist1 and Vimentin are upregulated in CRC tissue compared to the adjacent normal tissues. The qPCR data of E-cadherin, Twist1, and Vimentin mRNA expression in CRC tissue has already been published in other studies(Christou et al., 2017; Lazarova and Bordonaro, 2016; Zhu et al., 2015). It was found that E-cadherin is downregulated, while Twist1 and Vimentin are upregulated in CRC tissue compared to the adjacent normal tissues. The analysis of mRNA expression data obtained from colorectal cancer samples and normal samples in the publicly available databases TCGA and GTEx also revealed a significant downregulation of _Hes_4 expression in colorectal cancer tissues, which will be our next research objective.

(9) Some statements are inconsistent probably due to grammatical errors. (For example, some High/low may be reversed in lines 234-244.)

We apologize for these mistakes. We have made corrections to this section in the manuscript.

Reviewer #2 (Public Review):

Summary:

Using in vitro and in vivo approaches, the authors first demonstrate that BEST4 inhibits intestinal tumor cell growth and reduces their metastatic potential, possibly via downstream regulation of TWIST1.

They further show that HES4 positively upregulates BEST4 expression, with direct interaction with BEST4 promoter region and protein. The authors further expand on this with results showing that negative regulation of TWIST1 by HES4 requires BEST4 protein, with BEST4 required for TWIST1 association with HES4. Reduction of BEST1 expression was shown in CRC tumor samples, with correlation of BEST4 mRNA levels with different clinicopathological factors such as sex, tumor stage, and lymph node metastasis, suggesting a tumor-suppressive role of BEST4 for intestinal cancer.

Strengths:

• Good quality western blot data.

• Multiple approaches were used to validate the findings.

• Logical experimental progression for readability.

• Human patient data / In vivo murine model / Multiple cell lines were used, which supports translatability / reproducibility of findings.

We sincerely thank Reviewer #2 for constructive feedback on this work

Weaknesses:

(1) Interpretation of figures and data (unsubstantiated conclusions).

We apologize for this confusing presentation. We have made corrections to this section in the manuscript.

(2) Figure quality.

We apologize for the poor quality of the figures. The figure resolution was drastically reduced during the conversion of the manuscript to pdf on publisher web site. The figures have been re-uploaded and we have once again confirmed that each image has a resolution exceeding 300dpi.

(3) Figure legends lack information.

Sincere thanks for catching this issue. We have provided detailed figure legends including supplementary figure legends on pages 36-43 of the manuscript. We have rechecked this section and made improvements and additions.

(4) Lacking/shallow discussion.

We apologize for our shallow discussion. We have supplemented and improved some parts of the discussion

(5) Requires more information for reproducibility regarding materials and methods.

Sincere thanks for catching this issue. We have provided detailed information for reproducibility regarding materials and methods on pages 18-29; 43-47 of the manuscript. We have rechecked this section and made improvements and additions.

Recommendations for the authors:

Reviewer #1 (Recommendations For The Authors):

We sincerely thank Reviewer #1 for constructive feedback on this work.

Minor comments:

(1) Line 73: "Variant 4" is not precise. The term "variant" should mean mutation in the gene or different transcription.

We apologize for using an inaccurate expression. We have now changed Variant 4 to Bestrophin 4.

(2) Line 78. Is it correct that BEST4+ cells coexist with Hes4+ cells?

According to the previous study that published in Nature (Parikh et al., 2019), BEST4+ cells originate from the absorptive lineage and express the transcription factors Hes4. Additionally, we also observed the nuclear co-localization of BEST4 and Hes4 in HCT116 cells through immunofluorescence staining (Figure 3E)

(3) Line 85. The reason "Best4 may be associated with Twist1" is unclear.

We apologize for the lack of clarity in our previous statement. In a recent analysis utilizing single cell RNA-sequencing, it was discovered that a subset of mature colonocytes expresses BEST4 (Parikh et al., 2019). Additionally, this subset coexists with hairy/enhancer of split 4 positive (Hes4+) cells (Parikh et al., 2019). Previous research has demonstrated the antagonistic role of Hes4 in regulating Twist1 through protein-protein interaction, which governs the differentiation of bone marrow stromal/stem cell lineage (Cakouros et al., 2015). Based on these findings, we speculate that there may be an interactive regulation between BEST4/Hes4/Twist1, potentially influencing the process of cell polarity during epithelial-mesenchymal transition in colorectal cancer. We have made corrections to this section in the manuscript.

(4) Line 87. Grammatical error (Establishing the role BEST4).

We apologize for the grammatical error of this section. We have rectified the issue in the manuscript.

(5) Please clarify the reason the authors do not show any data of BEST4-overexpressing Caco2 cells in Figure 2?

We apologize for our negligence in not adding this data to in Figure 2. It has now been fully supplemented.

(6) In line 145, the authors did not show any tumorigenic properties.

We apologize for this confusing presentation. We have made corrections to this section in the manuscript.

(7) Figure 3 shows 1) HES4 regulates BEST4 promotor activity, and 2) HES4 and BEST4 colocalized in nuclei, but these are very different biological processes. Please clarify how these two relate to each other.

Trajectory analysis identifies the basic helix-loop-helix (bHLH) transcription factors Hairy/enhancer of split 4 (Hes4)-expressing colonocytes (Hes4+) in BEST4-expressing colonic epithelial lineage (BEST4+). Although they are very different biological processes, the recent identification of a heterogeneous BEST4+ and Hes4+ subgroup in a human colonic epithelial lineage (Parikh et al., 2019) led us to consider their potential role in regulating CRC progression. We firstly observed a responsive upregulation of both endogenous BEST4 mRNA and protein levels in Hes4 overexpression cells compared to the control transfectant, indicating that Hes4 is a potential upstream activator regulating BEST4 functional. We then confirmed that Hes4 interacted with BEST4, binding directly to its upstream promoter at the region of 1470-1569 bp enhancing its promoter activity as analysed by Co-IP, dual-luciferase assay and ChIP-qPCR, respectively. Essentially, they were co-localized in the nucleus, as shown in immunofluorescence staining after the transient co-transfection of Hes4 and BEST4 into HCT116, therefore indicating that BEST4 interacts with Hes4 at both transcriptional and translational levels (Figure 3; Figure 3-supplemental figure 1)

(8) In line 182-185, please clarify the reason BEST4 mediates the inhibition of the Twist 1 promotor activity by Hes4.

Because a step of Hes4 in committing to human bone marrow stromal/stem cell lineage-specific development is mediated by Twist1 downregulation (Cakouros et al., 2015), with evidence of direct interaction between BEST4 and Hes4 observed in HCT116, it is plausible that they could exploit Twist1 to regulate EMT. In the present study, we found that Twist1 colocalized with BEST4 in the nucleus, and their interaction destabilized Twist1 and significantly inhibited EMT induction. Hes4 caused the same effect; however, it required intermediation through BEST4. Although the mechanistic insights of their intercorrelation remain to be elucidated, the present study identified the axis of Hes4-BEST4-Twist1 governing the development of CRC, at least partially by counteracting EMT induction

(9) In line 205, please rephrase "BEST4-mediated upstream Hes4" to be clearer.

We apologize for this confusing presentation. We have made corrections to this section in the manuscript.

Reviewer #2 (Recommendations For The Authors):

We sincerely thank Reviewer #2 for constructive feedback on this work

Major Comments:

(1) The general quality of the figures requires improvement (text in some figures is illegible, and the resolution of the images is low) with more proofreading of the text for clarity. In addition, the resolution of the histology in Fig 2K does not allow a proper evalution of the data.

We apologize for the poor quality of the figures. The figure resolution was drastically reduced during the conversion of the manuscript to pdf on publisher web site. The figures have been re-uploaded and we have once again confirmed that each image has a resolution exceeding 300dpi. Meanwhile, the Figure 2K was further enhanced and expanded.

(2) While the authors show that the HES4/BEST4 complex interacts with the TWIST1 protein, they do not expand on the mechanisms underpinning the post-translational or transcriptional regulation of TWIST1. We would like the authors to prove or further speculate on the mechanisms behind this regulation in the discussion.

Our present study showed that BEST4 inhibited EMT in conjunction with downregulation of Twist1 in both HCT116 and Caco2 CRC cell lines. A previous study has shown an antagonist role of Hes4 in regulating Twist1 via protein-protein interaction that controls the bone marrow stromal/stem cell lineage differentiation (Cakouros et al., 2015). We speculate a possible interactive regulation between Hes4/BEST4/Twist1 by which they deter the process of cell polarity during EMT in CRC. In the present study, we found that BEST4 mediates the inhibition of the Twist1 both in transcription and translation level by Hes4. Twist1 colocalized with BEST4 in the nucleus, and their interaction destabilized Twist1 and significantly inhibited EMT induction. Hes4 caused the same effect; however, it required intermediation through BEST4. The present study identified the axis of Hes4-BEST4-Twist1 governing the development of CRC, at least partially by counteracting EMT induction. We agree that further studies to elucidate mechanistic insights of their intercorrelation are needed that are beyond the scope of the current work.

(3) The authors need to show or argue that why TWIST1 is necessary for the phenotypes observed, e.g. metastasis/proliferation.

We apologize for the lack of clarity in articulating this question. The process of EMT transforms epithelial cells exhibiting a spindle fibroblast-like morphology, leading to the acquisition of mesenchymal characteristics and morphology, enabling these cells to acquire invasive and migratory abilities, with expression switching epithelial E-cadherin and Zo-1 to mesenchymal vimentin (Dongre and Weinberg, 2019). When diagnosed in advanced stages, EMT may occur as CRC metastasize to distal organs (Pastushenko and Blanpain, 2019; Sunlin Yong, 2021; Yeung and Yang, 2017; Zhang et al., 2021).The whole process is regulated by transcriptional factors of the Snail family and Twist1(Dongre and Weinberg, 2019). Twist1 (a basic helix-loop-helix transcription factor) reprograms EMT by repressing the expression of E-cadherin and ZO-1 (Nagai et al., 2016; Yang et al., 2004) and simultaneously inducing several mesenchymal markers, typically vimentin (Bulzico et al., 2019; Meng et al., 2018; Nagai et al., 2016; Yang et al., 2004), which is a pivotal predictor of CRC progression (Vesuna et al., 2008; Yang et al., 2004; Yusup et al., 2017; Zhu et al., 2015).Overexpression of Twist1 significantly enhances the migration and invasion capabilities of colorectal cancer cells; furthermore, it is closely associated with metastasis and poor prognosis in patients with colorectal cancer(Yusup et al., 2017; Zhu et al., 2015). We have supplemented and improved these parts of the introduction and discussion.

(4) The authors sufficiently prove that HES4/BEST4 regulates TWIST1 downregulation, however, we believe the findings are not enough to show *direct* regulation (refer also to line 273). At least rephrasing the conclusions would be adequate, also while referring to the working model depicted in Fig. 5G.

We apologize for this inaccurate presentation. Although the interaction may not be direct, our co-immunoprecipitation (CO-IP) results demonstrated nuclear colocalization of Twist1 and BEST4 (Figure 4D; Figure 4-supplemental figure 1A). Furthermore, their interaction destabilized Twist1 and significantly inhibited the induction of EMT. We have made corrections to this section in the manuscript.

(5) The discussion is very short and not satisfactory; is BEST4 an evolutionary conserved protein (besides the channel region)? Any speculation on which domain(s) is(are) important for the interaction with HES4 and TWIST1? How do the findings in the current study compare with recent, potentially contradicting data indicating a pro-tumorigenic function of BEST4 for CRC, including its upregulation (and not downregulation) in malignant intestinal tissues, and activation of PI3K/AKT signaling (PMID: 35058597)?

We apologize for our shallow discussion. We have supplemented and improved some parts of the discussion. The bestrophins are a highly conserved family of integral membrane proteins initially discovered in Caenorhabditis elegans(Sonnhammer and Durbin, 1997). Homologous sequences can be found across animals, fungi, and prokaryotes, while they are absent in protozoans or plants(Hagen et al., 2005). Conservation is primarily observed within the N-terminal 350–400 amino acids, featuring an invariant motif arginine-phenylalanine-proline (RFP) with unknown functional properties (Milenkovic et al., 2008). Mutations in this region can lead to the development of vitelliform macular dystrophy. However, the C-terminus is a potential site for protein modification and function(Marmorstein et al., 2002; Miller et al., 2019). There is currently no further literature research on the functional roles of different domains of BEST4. Although the crucial domain for the interaction with HES4 and TWIST1 is yet to be determined, requiring further investigation for clarification, our findings demonstrate that Hes4 directly binds to the upstream promoter region of BEST4 at 1470-1569 bp, thereby enhancing its promoter activity. These results provide valuable insights for future research.

Sincere thanks for catching this publication to us. We carefully read this study and would like to point out a few things.

a) Firstly, the study demonstrated that BEST4 expression is upregulated in clinical CRC samples, which contradicts the results of other published studies except for our own research. RNA-seq of tissue samples from 95 human individuals representing 27 different tissues was performed to determine the tissue specificity of all protein-coding genes, and the results indicated that the BEST4 gene is predominantly expressed in the colon (Fagerberg et al., 2014). In addition, BEST4 was reported to be exclusively expressed by human absorptive cells and could be induced during the process of human absorptive cell differentiation(Ito et al., 2013). Recently, the research from Simmons’s group that published in Nature further proved that human absorptive colonocytes distinctly express BEST4 by single-cell profiling of healthy human colonic epithelial cells, and is dysregulated in colorectal cancer patients(Parikh et al., 2019). Furthermore, the analysis of RNA-seq expression data obtained from colorectal cancer samples and normal samples in the publicly available databases TCGA and GTEx also revealed a significant downregulation of BEST4 expression in colorectal cancer tissues, which is consistent with our research findings. The literature above demonstrates a close relationship between BEST4 and the normal function of the human colon, and provide evidence for their loss in colorectal cancer patients.

b) Their study showed an increased expression of BEST4 protein levels in colorectal cancer patients through Western Blot. However, the antibody they used was only suitable for IHC-P and not for Western Blot (Abcam , ab188823); . In our study, we also utilized WB technology to detect the expression of BEST4 in colorectal cancer tissues and adjacent normal tissues. The results revealed a decreased expression of BEST4 protein levels in colorectal cancer patients. The antibody we used was specifically designed for WB detection (1:800; LsBio, LS-C31133 https://www.lsbio.com/antibodies/best4-antibody-n-terminus-wb-western-ls-c31133/29602).

c) The study demonstrated an upregulation of BEST4 protein levels in colorectal cancer patients using immunohistochemistry (IHC). However, the expression of BEST4 was assessed in colorectal cancer tissues through IHC utilizing publicly available protein expression databases such as the Human Protein Atlas. Interestingly, this analysis revealed a minimal presence of BEST4 protein in colorectal cancer tissues (https://www.proteinatlas.org/ENSG00000142959-BEST4/pathology), contradicting their research findings but aligning with our own observations.

d) Literature based on single-cell genomics analysis reports that only OTOP2 and BEST4 genes are expressed in a subset of the normal colorectal epithelial cells but not the rest(Parikh et al., 2019). An inhibitory effect of OTOP2 on CRC has been recently shown BEST4, and the Otopetrin 2 (OTOP2), which encodes proton‐selective ion channel protein were reported to distinct expressed in normal absorptive colonocytes and colocalized with each other (Drummond et al., 2017; Ito et al., 2013; Parikh et al., 2019). OTOP2 has been recently demonstrated to have an inhibitory effect on the development of CRC via being regulated by wide-type p53(Qu et al., 2019), while the role of BEST4 in CRC is less well studied, that indicate the potential of BEST4 to inhibit colorectal cancer. The Gene set enrichment analysis (GSEA) conducted by them revealed a significant enrichment of gene signatures associated with oncogenic signaling and metastasis, such as the PI3K/Akt signaling pathway, in patients exhibiting higher BEST4 expression compared to those with lower BEST4 expression. However, our GSEA did not show any significant enrichment of the PI3K/Akt signaling pathway in patients with higher BEST4 expression compared to those with lower BEST4 expression. In contrast to their findings, our BEST4 overexpression cell line did not exhibit a significant increase in phosphorylated Akt levels. The present study concludes that our findings align with previous literature and public database analyses, providing evidence for the downregulation of BEST4 in colorectal cancer tissues and its potential as an anticancer agent. Discrepancies observed in other studies may be attributed to difference in experimental model, protocols, preparations or experimental conditions.

Minor Comments:

(1) Western blot data should be quantified.

Sincere thanks for catching this point to us. We have conducted a comprehensive quantification of all the Western Blot data and included the results in the supplementary file.

(2) Errors in labelling figures in the text should be corrected (Line 214 and more).

We apologize for these mistakes. We have made corrections to this section in the manuscript.

(3) The authors used the human HES4 gene, which is indicated with the incorrect nomenclature. The gene and protein nomenclature should be correctly used.

We apologize for these mistakes. We have made corrections to this section in the manuscript.

(4) Methods and Materials for certain assays should be further clarified; e.g transwell migration/invasion assays (reference to previous publication? transwell inserts used, etc.)

Sincerely thanks for catching this issue. We have implemented enhancements and updates to the respective sections.

(5) Figure 2K: Quality of histology is insufficient.

We apologize for the poor quality of the figures. The quality of Figure 2K was further enhanced and expanded.

(6) Figure 2K: Can the authors speculate on whether there is any increase in proliferation through BEST4-ko in HCT15 cells (with overexpression of BEST4 leading to reduced proliferation) and how this may impact the metastatic assay or engraftment/seeding onto the liver?

Our in vitro experiment demonstrated that the ablation of BEST4 in HCT-15 cells resulted in increased cell proliferation, clonogenesis, migration and invasion (Figures 1 and Figure 1-supplemental figure 1). These findings suggest that BEST4 knockout may potentially contribute to tumor proliferation in vivo; however, further research is required for confirmation. EMT transforms epithelial cells exhibiting a spindle fibroblast-like morphology, leading to the acquisition of mesenchymal characteristics and morphology, enabling these cells to acquire invasive and migratory abilities (Dongre and Weinberg, 2019). When diagnosed in advanced stages, EMT may occur as CRC metastasize to distal organs (Pastushenko and Blanpain, 2019; Sunlin Yong, 2021; Yeung and Yang, 2017; Zhang et al., 2021). Our study demonstrated that BEST4 inhibits EMT in colorectal cancer (CRC) both in vitro and in vivo. Conversely, ablation of BEST4 promotes EMT by upregulating the expression of EMT-related genes, thereby facilitating the metastasis of colorectal cancer cells to the liver.

(7) Figure 2L: Authors should indicate in the figure that the BEST4-rescued is at 0 (and not blank).

Sincerely thanks for catching this issue. We have made corrections to this section in the manuscript.

(8) Figure 3B: Authors should introduce the usage of the new LS174T cell line in the text.

Sincerely thanks for catching this issue. The human colorectal cancer cell line, LS174T, was selected for Hes4 knockdown due to its comparatively higher expression of Hes4 in comparison to other CRC cell lines. We have made corrections to this section in the manuscript.

(9) Figure 3F: Why is there less FLAG in the input, compared to the IP?

Sincerely thanks for catching this issue. Cell lysates (20 µg) were used for input, and 500ug for IP according to the manufacturer's protocols.

(10) Figure 5F-G: the quality of the figure is not good enough for interpretation.

Again, we apologize for poor quality of pictures due to manuscript conversion. We have made corrections to this section in the manuscript.

(11) Table 1: Conclusions made by the authors are wrong (lines 237-239); instead "high BEST4 expression more prevalent in females" and "low BEST4 expression more prevalent among CRC patients with advanced tumor stage". And how are low and high BEST4 expressions defined (the same applies to the data in Fig. 5F)?

We apologize for these mistakes, we set cutoff-high (50%) and cutoff-low (50%) values to split the high-expression and low-expression cohorts. We have made corrections to this section in the manuscript.

(12) In all Figure legends, there should be an indication of the type of statistical tests that were applied, as well as information on the number of independent experiments that were performed and provided the same results

Sincerely thanks for catching this issue. The types of statistical tests applied in the Materials and Method- Statistical analysis section are indicated. Information on the number of independent experiments used is provided in the figure legend section.

Reference

Bulzico, D., Pires, B.R.B., PAS, D.E.F., Neto, L.V., and Abdelhay, E. (2019). "Twist1 Correlates With Epithelial-Mesenchymal Transition Markers Fibronectin and Vimentin in Adrenocortical Tumors". Anticancer research 39, 173-175. 10.21873/anticanres.13094.

Cakouros, D., Isenmann, S., Hemming, S.E., Menicanin, D., Camp, E., Zannetinno, A.C., and Gronthos, S. (2015). "Novel basic helix-loop-helix transcription factor hes4 antagonizes the function of twist-1 to regulate lineage commitment of bone marrow stromal/stem cells". Stem Cells Dev 24, 1297-1308. 10.1089/scd.2014.0471.

Christou, N., Perraud, A., Blondy, S., Jauberteau, M.O., Battu, S., and Mathonnet, M. (2017). "E-cadherin: A potential biomarker of colorectal cancer prognosis". Oncol Lett 13, 4571-4576. 10.3892/ol.2017.6063.

Dongre, A., and Weinberg, R.A. (2019). "New insights into the mechanisms of epithelial-mesenchymal transition and implications for cancer". Nature reviews. Molecular cell biology 20, 69-84. 10.1038/s41580-018-0080-4.

Drummond, C.G., Bolock, A.M., Ma, C., Luke, C.J., Good, M., and Coyne, C.B. (2017). "Enteroviruses infect human enteroids and induce antiviral signaling in a cell lineage-specific manner". Proceedings of the National Academy of Sciences of the United States of America 114, 1672-1677. 10.1073/pnas.1617363114.

Fagerberg, L., Hallstrom, B.M., Oksvold, P., Kampf, C., Djureinovic, D., Odeberg, J., Habuka, M., Tahmasebpoor, S., Danielsson, A., Edlund, K., et al. (2014). "Analysis of the human tissue-specific expression by genome-wide integration of transcriptomics and antibody-based proteomics". Mol Cell Proteomics 13, 397-406. 10.1074/mcp.M113.035600.

Hagen, A.R., Barabote, R.D., and Saier, M.H. (2005). "The bestrophin family of anion channels: identification of prokaryotic homologues". Molecular membrane biology 22, 291-302. 10.1080/09687860500129711.

Ito, G., Okamoto, R., Murano, T., Shimizu, H., Fujii, S., Nakata, T., Mizutani, T., Yui, S., Akiyama-Morio, J., Nemoto, Y., et al. (2013). "Lineage-specific expression of bestrophin-2 and bestrophin-4 in human intestinal epithelial cells". PLoS One 8, e79693. 10.1371/journal.pone.0079693.

Lazarova, D.L., and Bordonaro, M. (2016). "Vimentin, colon cancer progression and resistance to butyrate and other HDACis". Journal of cellular and molecular medicine 20, 989-993. 10.1111/jcmm.12850.

Marmorstein, L.Y., McLaughlin, P.J., Stanton, J.B., Yan, L., Crabb, J.W., and Marmorstein, A.D. (2002). "Bestrophin interacts physically and functionally with protein phosphatase 2A". The Journal of biological chemistry 277, 30591-30597. 10.1074/jbc.M204269200.

Meng, J., Chen, S., Han, J.X., Qian, B., Wang, X.R., Zhong, W.L., Qin, Y., Zhang, H., Gao, W.F., Lei, Y.Y., et al. (2018). "Twist1 Regulates Vimentin through Cul2 Circular RNA to Promote EMT in Hepatocellular Carcinoma". Cancer research 78, 4150-4162. 10.1158/0008-5472.Can-17-3009.

Milenkovic, V.M., Langmann, T., Schreiber, R., Kunzelmann, K., and Weber, B.H. (2008). "Molecular evolution and functional divergence of the bestrophin protein family". BMC evolutionary biology 8, 72. 10.1186/1471-2148-8-72.

Miller, A.N., Vaisey, G., and Long, S.B. (2019). "Molecular mechanisms of gating in the calcium-activated chloride channel bestrophin". eLife 8. 10.7554/eLife.43231.

Nagai, T., Arao, T., Nishio, K., Matsumoto, K., Hagiwara, S., Sakurai, T., Minami, Y., Ida, H., Ueshima, K., Nishida, N., et al. (2016). "Impact of Tight Junction Protein ZO-1 and TWIST Expression on Postoperative Survival of Patients with Hepatocellular Carcinoma". Digestive diseases (Basel, Switzerland) 34, 702-707. 10.1159/000448860.

Parikh, K., Antanaviciute, A., Fawkner-Corbett, D., Jagielowicz, M., Aulicino, A., Lagerholm, C., Davis, S., Kinchen, J., Chen, H.H., Alham, N.K., et al. (2019). "Colonic epithelial cell diversity in health and inflammatory bowel disease". Nature 567, 49-55. 10.1038/s41586-019-0992-y.

Pastushenko, I., and Blanpain, C. (2019). "EMT Transition States during Tumor Progression and Metastasis". Trends in cell biology 29, 212-226. 10.1016/j.tcb.2018.12.001.

Qu, H., Su, Y., Yu, L., Zhao, H., and Xin, C. (2019). "Wild-type p53 regulates OTOP2 transcription through DNA loop alteration of the promoter in colorectal cancer". FEBS open bio 9, 26-34. 10.1002/2211-5463.12554.

Sonnhammer, E.L., and Durbin, R. (1997). "Analysis of protein domain families in Caenorhabditis elegans". Genomics 46, 200-216. 10.1006/geno.1997.4989.

Sunlin Yong, Z.W., Tang Yuan, Chuang Cheng, Dan Jiang (2021). "Comparison of MMR protein and Microsatellite Instability Detection in Colorectal Cancer and Its Clinicopathological Features Analysis". Journal of Medical Research 50, 61-66. 10.11969/j.issn.1673-548X.2021.05.015

Vesuna, F., van Diest, P., Chen, J.H., and Raman, V. (2008). "Twist is a transcriptional repressor of E-cadherin gene expression in breast cancer". Biochem Biophys Res Commun 367, 235-241. 10.1016/j.bbrc.2007.11.151.

Yang, J., Mani, S.A., Donaher, J.L., Ramaswamy, S., Itzykson, R.A., Come, C., Savagner, P., Gitelman, I., Richardson, A., and Weinberg, R.A. (2004). "Twist, a master regulator of morphogenesis, plays an essential role in tumor metastasis". Cell 117, 927-939. 10.1016/j.cell.2004.06.006.

Yeung, K.T., and Yang, J. (2017). "Epithelial-mesenchymal transition in tumor metastasis". Molecular oncology 11, 28-39. 10.1002/1878-0261.12017.

Yusup, A., Huji, B., Fang, C., Wang, F., Dadihan, T., Wang, H.J., and Upur, H. (2017). "Expression of trefoil factors and TWIST1 in colorectal cancer and their correlation with metastatic potential and prognosis". World journal of gastroenterology 23, 110-120. 10.3748/wjg.v23.i1.110.

Zhang, N., Ng, A.S., Cai, S., Li, Q., Yang, L., and Kerr, D. (2021). "Novel therapeutic strategies: targeting epithelial-mesenchymal transition in colorectal cancer". The Lancet. Oncology 22, e358-e368. 10.1016/s1470-2045(21)00343-0.

Zhu, D.J., Chen, X.W., Zhang, W.J., Wang, J.Z., Ouyang, M.Z., Zhong, Q., and Liu, C.C. (2015). "Twist1 is a potential prognostic marker for colorectal cancer and associated with chemoresistance". American journal of cancer research 5, 2000-2011.

Version 2

Abstract

Bestrophin isoform 4 (BEST4) is a newly identified subtype of the calcium-activated chloride channel family. Analysis of colonic epithelial cell diversity by single cell RNA-sequencing has revealed the existence of a cluster of BEST4+ mature colonocytes in humans. However, if the role of BEST4 is involved in regulating tumour progression remains largely unknown. In this study, we demonstrate that BEST4 overexpression attenuates cell proliferation, colony formation, and mobility in colorectal cancer (CRC) in vitro, and impedes the tumor growth and the liver metastasis in vivo. BEST4 is coexpressed with hairy/enhancer of split 4 (Hes4) in the nucleus of cells, and Hes4 signals BEST4 by interacting with the upstream region of the BEST4 promoter. BEST4 is epistatic to Hes4 and downregulates Twist1, thereby inhibiting epithelial-to-mesenchymal transition (EMT) in CRC. Conversely, knockout of BEST4 using CRISPR/Cas9 in CRC cells revitalises tumor growth and induces EMT. Furthermore, the low level of the BEST4 mRNA is correlated with advanced and the worse prognosis, suggesting its potential role in regulating CRC progression.

Introduction

Colorectal cancer (CRC) is a common tumour worldwide. A steady increase in the morbidity and mortality of CRC has been reported (Rawla et al., 2019). When diagnosed in advanced stages, epithelial-mesenchymal transition (EMT) may occur as CRC metastasize to distal organs (Pastushenko and Blanpain, 2019; Sunlin Yong, 2021; Yeung and Yang, 2017; Zhang et al., 2021). EMT is a reprogramming process in which epithelial E-cadherin and ZO-1 are suppressed, and mesenchymal N-cadherin and vimentin are induced, transcriptionally mediated by Twist and the Snail family (Dongre and Weinberg, 2019). Overexpression of Twist1 significantly enhances the migration and invasion capabilities of colorectal cancer cells; furthermore, it is closely associated with metastasis and poor prognosis in patients with colorectal cancer (Yusup et al., 2017; Zhu et al., 2015).

The inhibition of EMT in breast cancer and prostate cancer has been associated with calcium-activated chloride channels (CaCCs) (Porretti et al., 2018; Walia et al., 2012), leading to various evaluations of CaCCs as a potential for cancer therapy (Li et al., 2017; Miotto and Struhl, 2006; Qu et al., 2019; Sui et al., 2014). The bestrophin (BEST) chloride channel, which is a member of a recently identified gene family, encodes several integral membrane proteins expressed on the basolateral membranes of epithelial cells; they regulate CaCCs to maintain homeostasis (Marmorstein et al., 2009; Tsunenari et al., 2003). Although there are four human evolutionarily-related genes (BEST1–BEST4) (Miller et al., 2019; Tsunenari et al., 2003), BEST4 is expressed predominantly in the colon (Fagerberg et al., 2014), where it gates electrolyte transportation in human intestinal epithelial cells (Ito et al., 2013). However, its role and the mechanism in regulating the development of CRC are currently unknown.

In a recent analysis based on single cell RNA-sequencing analysis, it was discovered that a group of mature colonocytes expresses BEST4 (Parikh et al., 2019), and the subset of this group coexists with hairy/enhancer of split 4 positive (Hes4+) cells (Parikh et al., 2019). Hes4 belongs to a family of seven Hes genes (Hes1–7) that encodes a transcription factor with a basic helix-loop-helix motif. It is known to play a critical role in determining the fate and differentiation of progenitor cells during the development of various organs. The previous study has demonstrated the antagonistic role of Hes4 in regulating Twist1 through protein-protein interaction, which governs the differentiation of bone marrow stromal/stem cell lineage ((Cakouros et al., 2015). Inhibiting the Twist1 transcriptional factor has been shown to mediate commitment to the differentiation of human bone marrow stem cells, as reported by several studies (Cakouros et al., 2015; El Yakoubi et al., 2012; Murato and Hashimoto, 2009; Nichane et al., 2008). Given this information, it is tempting to speculate that BEST4 may be associated with Hes4 and Twist1 in regulating EMT during CRC progression.

The objectives of the present study are as follows: (1) to establish the role of BEST4 in CRC growth both in vitro and in vivo; (2) to determine the underlying molecular mechanisms by which BEST4 interacts with Hes4 and Twist1, thereby inducing EMT; and (3) to investigate the correlation between BEST4 expression and prognosis of CRC.

Results

BEST4 inhibits CRC proliferation, clonogenesis, migration, and invasion in vitro

To evaluate the effect of BEST4 on tumour growth, we constructed BEST4-expressing HCT116 and Caco2 CRC cell lines (Figure 1-figure supplement 1A-1C) and showed that BEST4 overexpression halved cell proliferating rates of their respective empty vector (EV) controls when they were monitored in live and analysed using InCucyte (Figures 1A and 1B). This was accompanied by decreased cell viability (Figure 1-figure supplement 1D and 1E). To determine the causal role of BEST4 in CRC tumorigenesis, we knocked out the BEST4 in HCT-15 using a CRISPR/Cas9 system (Figure 1-figure supplement 1F-H). Consequently, there was a 50% increase in proliferation rates and viability compared with the parental control (Figures 1C and 1D; Figure 1-figure supplement 1I). Rescued expression of BEST4 was able to reverse the observed effects on HCT-15 (Figure 1D; Figure 1-figure supplement 1I).

BEST4 inhibits CRC cell proliferation, clonogenesis, migration, and invasion in vitro. Overexpression of BEST4 decreased proliferation of HCT 116 (A) and Caco2 (B) cells as determined by the IncuCyte confluence assay. (C) Viability of three individual BEST4-deleted clones as determined by a CCK-8 assay. (D) BEST4 deletion significantly enhanced cell viability compared with cells transduced with EV-gRNA control; the reintroduction of BEST4 resulted in suppressed cell growth as determined by IncuCyte confluence analysis. (E) Expression of BEST4-HA in HCT116 and Caco2 cells resulted in more colonies than cells transduced with EV plasmids (left panel); colonies were counted and analysed as shown (right panel). (F) A colony formation assay was performed to evaluate the responses of HCT-15 cells following BEST4 deletion and reintroduction (left panel); cell colonies were counted and analysed as shown (right panel). (G) Heterologous expression of BEST4 in HCT116 cells suppressed invasion and migration (upper panel, scale bar, 200 μm); cells that passed through the membrane were counted and compared (lower panel). (H) BEST4 deletion in HCT-15 cells promoted invasion, whereas reintroduction of BEST4 expression resulted in the inhibition of HCT-15 cell invasion and migration (upper panel, scale bar, 200 μm). Cells that passed through the membrane were counted and compared (lower panel). Data shown are the result of at least three independent experiments, with the mean ± SEM; *P<0.05, **P<0.01 vs EV or WT.

In contrast to the controls, BEST4 overexpression decreased colony formations of HCT116 and Caco2 by 60% and 70%, respectively (Figure 1E). While BEST4 deletion increased the number of colonies by five-fold in HCT-15 (Figure 1F), the rescued expression counteracted its enhancement (Figure 1F).

Furthermore, overexpression of BEST4 in HCT116 inhibited transwell migration and invasion by 70% and 80%, respectively, compared to EV controls (Figure 1G). But BEST4 ablation in HCT-15 increased cell migration and invasion by two-fold and three-fold, respectively. These pro-tumor effects on HCT-15 were also reversible when BEST4 expression was rescued (Figure 1H).

Collectively, these findings suggest the functional inhibitory effects of BEST4 on CRC development in vitro.

BEST4 deters EMT in CRC in vitro and in vivo

Because EMT initiation is a critical process in tumour progression (Acloque et al., 2009), we evaluated the effect of BEST4 on EMT using qPCR and found that BEST4 expression upregulated CDH1 and ZO-1 and downregulated vimentin and Twist1 in HCT116 compared with the control (p < 0.05) (Figures 2A). Conversely, knockout of BEST4 in HCT15 downregulated CDH1 and ZO-1 and upregulated vimentin and Twist1. Rescued expression of BEST4 in HCT-15 reversed these gene alterations (Figures 2B). Changes of these genes were consistent with their corresponding protein expression as analysed by immunoblotting (Figures 2C and 2D; Figure 2-figure supplement 1A-1C).

BEST4 deters EMT in CRC in vitro and in vivo. (A) Expression of mRNAs encoding EMT-related genes as determined by qPCR in HCT116 cells transfected with BEST4-HA or EV. (B) As determined by qPCR, the expression of mRNAs encoding EMT markers in BEST4-deleted and BEST4-restored HCT-15 cells. (C) Protein expression of EMT-related genes was evaluated by western blotting of lysates of HCT116 cells transfected with BEST4-HA or EV. (D) Western blotting determined the levels of immunoreactive EMT markers in BEST4-deleted and BEST4-restored HCT-15 cells. (E) Growth of xenograft tumours in BALB/c nude mice resulting from the injection of HCT116 cells stably-transduced with BEST4-HA was significantly diminished compared with those resulting from HCT116 cells transduced with EV alone (eight mice per group). (F) The histogram represents the mean weights of tumours isolated from the HCT116-BEST4-HA and HCT116-EV groups. (G) Tumours from the HCT116-BEST4-HA and HCT116-EV groups were sectioned and subjected to immunohistochemical staining to detect HA and human Ki67; scale bar=50 μm. (H) Mean percentage of Ki67-positive staining in each group. (I) Representative western blot documenting protein levels of EMT markers in individual HCT116-BEST4 and HCT116-EV xenograft tumours. *P<0.05, **P<0.01. Data from at least three independent experiments are presented as the mean ± SEM. (J-L) Intrasplenical injections of HCT-15 cell lines with EV-gRNA control, BEST4-gRNA or BEST4-Rescued (n = 3 per group). After 28 days, the animals were sacrificed and numbers of metastatic nodules in the liver were counted, and the liver tissues were fixed for sectioning and H&E staining; T, Tumour.Data are presented as the mean ± SEM. **P<0.01 vs EV-gRNA.

Next, we subcutaneously implanted BEST4-HA-expressing HCT116 and EV control cell lines into BALB/c nude mice and monitored tumour growth weekly. When they reached the maximum allowable volumes (day 32), the animals were culled, and tumours were harvested. Essentially, the sizes and weights of tumours in BEST4 overexpression group were only half of the EV control (Figures 2E and 2F), in conjunction with the similar magnitude reduction of Ki67+ cells as analyzed by immunohistochemistry (Figure 2G and 2H). Further analysis of the HCT116 tumour tissue lysates showed that BEST4 deterred EMT by upregulating E-cadherin and, downregulating vimentin and Twist1 (Figures 2I; Figure 2-figure supplement 1D).

We also evaluated the inhibitory role of BEST4 in a model of CRC to the liver metastasis by intrasplenically injecting HCT-15 cell lines with BEST4 knockout (BEST4gRNA) or the wild-type control (gRNA) or the knockout with the rescue (BEST4-Rescued) into BALB/c nude mice. We observed that there were 2-fold greater of the liver metastatic nodules in the BEST4 deficient tumors than the control (Fig. 2J-L). Conversely, the reconstituted BEST4 expression had no visible metastatic nodules in the liver, and the pathological analysis of the tissue sections by H&E staining also confirmed no detectable metastatic loci in the tissue sections (Fig. 2J-L).

These findings indicate the role of BEST4 in suppressing CRCgrowth, through counteracting EMT induction in models of in vitro and in vivo.

Hes4 upstream regulation of BEST4

Given the co-expression of BEST4+ and Hes4+ in a human colonic epithelial lineage (Parikh et al., 2019), we sought to investigate their biological interactions during tumour growth. The human CRC cell line, HCT116, was chosen for Hes4 overexpression due to its relatively lower expression of Hes4 compared to other CRC cell lines. Similarly, the LS174T cell line derived from human CRC was selected for Hes4 knockdown because it exhibited comparatively higher expression of Hes4 in comparison to other CRC cell lines (Figure 3-figure supplement 1A). Upon transfecting the Flag-Hes4 plasmid DNA into HCT116, we observed a responsive upregulation of both endogenous BEST4 mRNA and protein levels compared to the control transfectant (Figure 3A; Figure 3-figure supplement 1B and 1C). This intrinsic association was further supported by knocking down the endogenous Hes4 with two pairs of shRNAs in LST174 that resulted in downregulation of endogenous BEST4 (Figure 3B; Figure 3-figure supplement 1D and 1E).

Molecular regulation of BEST4 expression by Hes4. (A) Endogenous BEST4 mRNA and protein levels in Hes4-overexpressing HCT116 cells were detected by qPCR and western blotting, respectively. (B) Endogenous BEST4 mRNA and protein levels in LS174T cells after shRNA-mediated Hes4 knockdown as detected by qPCR and western blotting, respectively. (C) Detection of BEST4 promoter activity in Hes4-overexpressing HCT116 cells using a dual-luciferase reporter assay. (D) As determined by ChIP-qPCR, Fold-enrichment of the BEST4 promoter region in Flag-ChIP samples from Hes4-overexpressing HCT116 cells. Data were normalized using a fold-enrichment method (i.e., ChIP signals divided by control IgG signals). The DHFR 5’ UTR was used as a negative control (upper panel). The primer sets that target the BEST4 promoter in the ChIP-qPCR assays are as illustrated; +1 marks the transcriptional start site of BEST4, and P1, P2, P3, and P4 represent primer locations (lower panels). (E) Immunofluorescence staining documents the colocalization of BEST4 (green) and Hes4 (red) in HCT116 cells based on detection of their specific tags; scale bar, 20 μM. (F) Co-immunoprecipitation of nuclear extracts with specifically-tagged BEST4 and Hes4 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (G) Detection of BEST4 promoter activity in Hes4-overexpressing HCT116 cells after BEST4 knockdown through a dual-luciferase reporter assay. Data shown are the result of at least three independent experiments, with the mean ± SEM; *P<0.05, **P<0.01 vs EV

To explore how Hes4 regulates BEST4 expression at the transcriptional level, we transfected a BEST4 promoter-driven luciferase DNA construct into Hes4-expressing HCT116 and assessed the promoter activity using a dual-luciferase assay. Our results showed a four-fold increase in the promoter activity compared to the EV control (Figure 3C), Furthermore, ChIP-qPCR analysis using a Flag antibody to IP for Hes4 revealed a twelve-fold enrichment of the P3 region upstream of the BEST4 transcriptional start site compared to the control (Figure 3D). Interestingly, BEST4 overexpression in HCT116 cells did not affect Hes4 mRNA expression as quantified by qPCR (Figure 3-figure supplement 1F), suggesting that Hes4 regulates BEST4 expression upstream. This speculation is supported by immunofluorescence staining, where we observed nuclear co-localization of BEST4 (green) and Hes4 (red) in HCT116 cells co-transfected with BEST4-HA and Flag-Hes4 plasmid DNAs, along with additional cytoplasmic expression of BEST4 (Figure 3E).

To evaluate the association of BEST4 with Hes4 at the translational level, we co-transfected their HA-tagged BEST4 and Flag-Hes4 plasmid DNAs into HEK293 cells, along with the respective single transfectant control. By conducting IP with antibodies specific to Flag or HA, we showed that BEST4 and Hes4 were reciprocally copurified from the nuclear protein lysates, but not with IgG controls (Figure 3F).

Collectively, these findings indicate that BEST4 interacts with Hes4 at both transcriptional and translational levels.

BEST4 relays Hes4 signal and downregulates Twist1 leading to EMT inhibition independent of the channel function in CRC

Because a step of Hes4 in committing to human bone marrow stromal/stem cell lineage-specific development is mediated by Twist1 downregulation (Cakouros et al., 2015), with evidence of direct interaction between BEST4 and Hes4 observed in HCT116, it is plausible that they could exploit Twist1 to regulate EMT. To test this notion, we transfected a Twist1 promoter-driven luciferase DNA construct into HCT116. In comparison with the EV control, Flag-Hes4 or BEST4-HA transfectants significantly decreased Twist1 promoter activity by almost half, as evaluated by the dual-luciferase assay (Figure 4A). Essentially, the BEST4 transfectant enhanced inhibition of the Twist promoter by 70% in Hes4-expressing HCT116 (Figure 4B; Figure 4-figure supplement 1A), hence suggesting that BEST4 mediates the inhibition of the Twist1 promoter activity by Hes4. This effect was also observed when endogenous Hes4 was knocked down using shRNAs in HCT116 cells transfected with BEST4-HA plasmid DNA (Figure 4C).

BEST4 relays the Hes4 signal and downregulates Twist1 expression to counteract EMT induction in CRC (A) Detection of Twist1 promoter activity in Hes4-overexpressing or BEST4-overexpressing HCT116 cells through a dual-luciferase reporter assay. (B) Detection of Twist1 promoter activity in Hes4-overexpressing HCT116 cells after BEST4 knockdown through a dual-luciferase reporter assay. (C) Detection of Twist1 promoter activity in HCT116 cells after shRNA-mediated Hes4 knockdown and combination with BEST4-overexpressing using a dual-luciferase reporter assay. (D) Co-immunoprecipitation of nuclear extracts with specifically-tagged BEST4 and Twist1 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (E) Co-immunoprecipitation of nuclear extracts with specifically-tagged Hes4 and Twist1 as determined by immunoblotting. Lamin B1 served as a nuclear protein control. (F) Expression of EMT markers in Hes4-overexpressing HCT116 cells. (G) Expression of EMT markers in LS174T cells after shRNA-mediated Hes4 knockdown. (H) Expression of EMT markers in Hes4-overexpressing HCT116 cells after BEST4 knockdown. (I) Expression levels of EMT markers in BEST4-overexpressing LS174T cells after Hes4-knockdown; SCR, scrambled siRNA.

The association of BEST4 with the Twist1 promoter activity was also evidenced by their nuclear colocalization after transfecting BEST4-HA and Myc-Twist1 plasmid DNAs into HCT116 (Figure 4-figure supplement 1B). Co-IP with antibodies to Myc or HA showed that they were copurified from the nuclear protein lysates, but not with the IgG controls from the transfectant cell lysates (Figure 4D; Figure 4-figure supplement 1B). Additionally, the knockdown of endogenous BEST4 in Hes4-expressing HCT116 cells substantially decreased Flag-Hes4 coprecipitation from the nuclear protein lysates, while Myc-Twist1 expression remained constant, as determined by co-IP with antibodies to Flag or My (Figure 4E; Figure 4-figure supplement 1C).

We then investigated the impact of Hes4 expression on EMT induction by overexpressing Hes4 in HCT116 cells. Our results showed there were upregulation of ZO-1 and E-cadherin epithelial molecules, and downregulation of Twist1 protein (Figure 4F; Figure 4-figure supplement 2A) and the vimentin mRNA (Figure 4-figure supplement 1D). The vimentin protein appeared to be undetectable in HCT116, which was consistent with a previous report (Roger et al., 2010). Nevertheless, knocking down endogenous Hes4 in LS174T cells using shRNAs targeting two Hes4 domains caused the opposite effect (Figure 4G; Figure 4-figure supplement 2B).

To determine if BEST4 is downstream signal that relays Hes4 to regulate Twist1 expression and consequently EMT induction, we knocked down endogenous BEST4 with siRNAs in Hes4-expressing HCT116 and showed the corresponding downregulation of E-cadherin and ZO-1, with upregulation of Twist1 protein and the vimentin mRNA, as analyzed by immunoblotting and qPCR (Figure 4H; Figure 4-figure supplement 2C; Figure 4-figure supplement 1ED). The opposite was true when BEST4 was overexpressed in LS174T (Figure 4I; Figure 4-figure supplement 2D). Hes4Hence, inhibition of EMT induction by Hes4 is BEST4-mediated by downregulation of Twist1 expression in CRC

Given the physiological role of BEST4 plays in regulating chloride/calcium flux, we evaluated the channel functional effect on EMT induction. After respectively incubating BEST4-expresing HCT116 and the EV control with 300μM DIDS (a broad blocker of chloride channel), or a gradient increase in doses of CaCCinh-A01 (a specific inhibitor of native calcium-activated chloride channels), or 1μM ionomycin (a calcium ionophore to activate the chloride channel) as published previously (Liu et al, 2015; Uwada et al, 2019), we showed that BEST4 significantly increased chloride/calcium fluxes and activated their exchanges and the expected inhibition by DIDS, CaCCinh-A01 or ionomycin (Figure 5-figure supplement 1A-1C). Through immunoblotting analysis, we recapitulated that BEST4 simultaneously upregulated both ZO-1 and E-cadherin, and downregulated Twist1. Essentially, the levels of these proteins remained constantly expressed when the cells were treated with DIDS or CaCCinh-A01 or ionomycin, respectively (Figure 5-figure supplement 1D-1F). Hence, these results suggest BEST4 protein-mediated EMT suppression is independent of its channel function in HCT116.

Correlation of the BEST4 with clinicopathology and outcomes of patients diagnosed with CRC

We showed evidence of the endogenous BEST4 mRNA and protein expression in HCT116 and LS174T CRC cell lines (Figures 3A and 3B); these findings prompted us to explore the potential clinically significant BEST4 expression in CRC. Initially with high-throughput whole transcriptome sequencing analysis of five pairs of CRCs and adjacent normal tissues (ANTs), we identified several significantly downregulated genes in CRC compared to ANTs; BEST4 was in the top four (Figures 5A and 5B). Further validation by qPCR in the paired tissues of 50 colorectal adenomas and 124 CRC showed that the BEST4 was expressed significantly less in adenomas and tumours than in ANTs (Figures 5C and 5D). Immunoblotting analysis of tissue lysates from five paired randomly selected samples showed that BEST4 protein was downregulated in CRC (Figures 5E; Figure 5-figure supplement 1G). Using public datasets of The Cancer Genome Atlas (TCGA) and the Genotype-Tissue Expression (GTEx), we measured BEST4 mRNA expression in CRC and matched normal tissues with the online Gene Expression Profiling Interactive Analysis (GEPIA) tool (http://gepia.cancer-pku.cn/). As shown in Figure 6-figure supplement 1A, the normal colorectal control tissues consistently expressed higher BEST4 than the CRC.

Correlation of the BEST4 mRNA expression with clinicopathology and outcomes of patients diagnosed with CRC. (A) Heatmap based on the top 100 differentially expressed genes (downregulated and upregulated) in CRCs compared with ANTs. (B) Volcano plots of RNA seq results showing all differentially expressed genes in CRC tissues compared with ANTs based on the fold-change (|FC|≥L1) and P-value (P≤0.05). (C) Expression levels of BEST4 mRNA in 50 pairs of adenoma tissues compared with ANTs. (D) Expression levels of BEST4 mRNA in 124 pairs of CRC tissues compared with ANTs. (E) BEST4 protein levels in CRC and their matched counterparts were measured using western blotting. (F) Kaplan-Meier survival analysis according to BEST4 expression in 124 patients with CRC. The difference was statistically significant based on the log-rank test (P<0.01). (G) A working model delineates the mechanism by which BEST4 is transcriptionally activated by Hes4 and suppressed EMT through Twist1 inhibition: a. the expression of BEST4 is regulated by interactions of its upstream promoter region with Hes4. BEST4 positively promotes the transcriptional activity of Hes4 on BEST4 by physically binding to Hes4 in a positive feedback loop; b. The complex formed by BEST4 and Hes4 interacts with Twist1 and inhibits the promoter activity of Twist1. Hes4 alone is insufficient to inhibit Twist1 promoter activity, and BEST4 is required. Inhibition of Twist1 promoter activity by Hes4 is BEST4-dependent c. The complex formed by BEST4 and Hes4 destabilized Twist1; the same effect caused by Hes4 required BEST4 intermediation. The Hes4-BEST4-Twist1 axis counteracts EMT induction. *P<0.05, **P<0.01; CRC, colorectal cancer; ANT, adjacent normal tissue; T, tumour.

We further evaluated the clinicopathological significance of BEST4 expression in CRC patients by examining its correlation with gender, tumour-node-metastases stage, and lymph node metastasis based on the eighth edition of the American Joint Committee on Cancer Staging Manual (M. B. Amin et al., Springer, 2017). Interestingly, low BEST4 mRNA expression in males was twice as high as in females (p=0.022, Table 1). Accordingly, low BEST4 mRNA expression correlated with more advanced stages (p=0.02, Table 1) and lymph node metastasis (between 0 and 2) (p=0.032, Table 1). Patients with high BEST4 expression had better overall survival than those with low expression (p<0.01, Figure 5F), which was confirmed by univariate survival analysis showing a lower risk of death (p<0.001, Table 2). Multivariate Cox regression analysis indicated that low levels of BEST4 mRNA were associated with poor prognosis of CRC patients (Hazard Ratio [HR], 0.285; 95% confidence interval, 0.157–0.606; P<0.001; Table 2).

After the significant reduction of the Hes4 mRNA expression through RNA sequencing analysis of our CRC patients (Figure 6-figure supplement 1B and 1C), we proceeded to investigate the connection between BEST4 and Hes4 in TCGA and GTEx (http://gepia.cancer-pku.cn/). Our findings revealed a positive correlation between these genes (R = 0.47, p<0.001) (Figure 6-figure supplement 1D), providing further evidence of their association in CRC. Furthermore, we conducted additional mining of TCGA or GTEx datasets using the GEPIA tool (http://gepia.cancer-pku.cn/) and observed a positive correlation between BEST4 and the CDH1 mRNA (R = 0.77, p<0.001), with a negative correlation with vimentin (R =–0.49, p<0.001) and Twist mRNA (R =–0.39, p<0.001)) (Figure 6-figure supplement 1E-G). These correlation analyses of RNA sequencing data from our patients and publicly available datasets underscore the association of low BEST4 expression with worse outcomes in malignant CRC.

Discussion

In cancer cell cultures and mouse tumour xenografts, the present study shows that BEST4 inhibits the development of CRC. An axis comprising Hes4/BEST4/Twist1 governs the induction of EMT in CRC. BEST4 interacts with Hes4 at the transcriptional and translational levels, and downregulates Twist1 expression, resulting in EMT inhibition but independent of its channel functions. Our findings support the notion in several ways: (1) Hes4 binds to the promoter region of BEST4; (2) BEST4 colocalizes with Hes4 and Twist1 in the nucleus of cells, and protein-protein interactions; (3) the BEST4 inhibitory role in EMT exhibits upregulation of epithelial ZO-1 and E-cadherin, and downregulation of mesenchymal vimentin and Twist1 in CRC; and finally (4) low BEST4 mRNA levels were significantly correlated with malignant lesions and worse outcomes of CRC patients. To the best of our knowledge, this is the first characterization of the role of BEST4 in suppressing CRC progression and the underlying molecular mechanisms.

CaCCs are expressed widely in several types of epithelial and endothelial cells and are classified as calcium-dependent chloride channels (e.g., anoctamin-1 [ANO1 or TMEM16]), chloride channel accessory proteins (CLCAs), and members of the BEST family. The latter is a recent addition to the class of molecularly defined chloride channels (Huang et al., 2012). Calcium-dependent chloride channels and CLCAs are differentially expressed in CRC and normal colon tissues, exerting pro- or anti-growth effects, while little is known of BEST family in CRC (Li et al., 2017; Sanders et al., 2012; Sui et al., 2014; Yang et al., 2015). There are four subtypes of the BEST family in mammals that assemble as pentamers to form Ca2+-activated Cl- channels and maintain cellular physiological functions (Marmorstein et al., 2009; Milenkovic et al., 2008; Tsunenari et al., 2003). Subtypes of BEST1-3 are responsible for vitelliform macular dystrophy, regulating the cilia of olfactory sensory neuronal activity; others regulate cGMP-dependent calcium-activated chloride conductance in vascular smooth muscle cells (Matchkov et al., 2008; Pifferi et al., 2009). An intrinsic function of the BEST4 gene in modulating CRC growth remains poorly illustrated. In the present study, we demonstrated that BEST4 functionally inhibits the development of CRC in vitro and in vivo. BEST4 is transcriptionally regulated and physically interacts with upstream Hes4, leading to downregulation of Twist1 and EMT suppression. This suppression is independent of physiological Ca2+-activated Cl- channels since inhibition of BEST4-associated Ca2+-and Cl- fluxes did not alter ZO-1/E-Cadherin and Twist1 protein expression.

The recent identification of a heterogeneous BEST4+ and Hes4+ subgroup in a human colonic epithelial lineage (Parikh et al., 2019) led us to consider their potential role in regulating CRC progression. Among the Hes family, which is associated with intestinal progenitor cells in adenoma transformation, Hes1 and Hes4 are a paralog pair, with other members more distantly related (Katoh and Katoh, 2004). While Hes1 has been reported to induce EMT and promote metastasis and chemoresistance in CRC (Sun et al., 2017; van Es et al., 2005; Yuan et al., 2015), Hes4 is identified by our present study capable of combating EMT induction in a BEST4-dependent manner that is regulated at both transcriptional and translational levels.

The process of EMT transforms epithelial cells exhibiting a spindle fibroblast-like morphology, leading to the acquisition of mesenchymal characteristics and morphology, enabling these cells to acquire invasive and migratory abilities, with expression switching epithelial E-cadherin and Zo-1 to mesenchymal vimentin (Dongre and Weinberg, 2019). When diagnosed in advanced stages, EMT may occur as CRC metastasize to distal organs (Pastushenko and Blanpain, 2019; Sunlin Yong, 2021; Yeung and Yang, 2017; Zhang et al., 2021).The whole process is regulated by transcriptional factors of the Snail family and Twist1(Dongre and Weinberg, 2019). Twist1 (a basic helix-loop-helix transcription factor) reprograms EMT by repressing the expression of E-cadherin and ZO-1 (Nagai et al., 2016; Yang et al., 2004) and simultaneously inducing several mesenchymal markers, typically vimentin (Bulzico et al., 2019; Meng et al., 2018; Nagai et al., 2016; Yang et al., 2004), which is a pivotal predictor of CRC progression (Vesuna et al., 2008; Yang et al., 2004; Yusup et al., 2017; Zhu et al., 2015). The Twist1 transcriptional factor plays a crucial role in inducing EMT, which contributes to the malignant lesions (Yang et al., 2004). Its physical interaction with Hes4 determines human bone marrow stromal/stem cell differentiation (Cakouros et al., 2015). Twist1, a basic helix-loop-helix transcription factor, represses the expression of E-cadherin and ZO-1 and induces several mesenchymal markers including vimentin, which is a pivotal predictor of CRC progression (Nagai et al., 2016; Yang et al., 2004) (Bulzico et al., 2019; Meng et al., 2018; Nagai et al., 2016; Vesuna et al., 2008; Yang et al., 2004; Yusup et al., 2017; Zhu et al., 2015). Overexpression of Twist1 significantly enhances the migration and invasion capabilities of colorectal cancer cells; furthermore, it is closely associated with metastasis and poor prognosis in patients with colorectal cancer(Yusup et al., 2017; Zhu et al., 2015). Despite Twist1 importance in CRC, little is known about how it is controlled during EMT induction. Our present study reveals that Twist1 colocalized and interacted with BEST4 in the nucleus of CRC HCT116 cells, leading to downregulation of Twist1 and inhibition of EMT. Hes4 also caused the same effect, but through intermediation with BEST4. Although the mechanistic insights of their interplay remain to be elucidated, the present study identifies the Hes4-BEST4-Twist1 axis that contributes to counter EMT in the development of CRC (Figure 5G).

Lastly, our analysis of correlations reveals the clinical significance of BEST4 expression in CRC. In particular, the mRNA levels of BEST4 were lower in tissues of both precancerous adenomatous lesions and CRC than ANTs. These alterations are significantly correlated with large tumour size, positive nodes, and poor overall survival, especially in male patients. Interestingly, a previous study conducted on a Chinese cohort reported an approximately 40% higher incidence of CRC in males than in females (Zhang et al., 2019). But it remains to be investigated whether sex hormone-related factors plays a role in the gender-specific downregulation of BEST4 and its impact on CRC in males (Yu et al., 2020).

In conclusion, the functional significance of BEST4 in CRC development and its interplay with other molecules is completely unknown. The present study demonstrates the role of BEST4 in inhibiting CRC proliferation, migration, and invasion both in models of in vitro and in vivo. Mechanically, BEST4 is epistatic to Hes4 for downregulating Twist1 and inhibits EMT in CRC. Therefore, we reveals a previously unknown mechanism of the Hes4-BEST4-Twist axis that restrains the progression of CRC.

Materials and Method

Clinical samples

A total of 124 samples of paired CRC and adjacent normal tissue and 50 samples of paired adenoma and ANT were collected randomly from clinical specimens from patients undergoing intestinal resections or upper gastrointestinal endoscopies at the Department of Gastrointestinal Surgery and Digestive Endoscopy Centre, West China Hospital, China, between January and December 2013. All patients were followed until December 2018 or until death. Samples from patients with malignant tumours in other organs, from patients who received preoperative chemotherapy or radiotherapy, and from patients with incomplete follow-up data were excluded. The survival time was calculated from the surgery date to the follow-up deadline (above) or until the date of death. The Ethics Committee of West China Hospital, Sichuan University (Sichuan, China) approved the study. All procedures were performed per the 1964 Declaration of Helsinki. Written informed consent was obtained from all participants.

Cell cultures and reagents

The human colon cancer cell lines Caco-2, HCT116, HCT-15, and LS174T were purchased from The American Type Culture Collection (Manassas, VA, USA). Cells were authenticated using short tandem repeat analysis performed within two years of receipt. Cells at passages >15 were not used. All cells were maintained in Dulbecco’s Modified Eagle’s medium (DMEM; Gibco, Waltham, MA, USA) supplemented with 10% foetal bovine serum (FBS), 100 U/mL penicillin, and 100 mg/mL streptomycin. Before each experiment, cells were provided with low glucose (1 g/L) DMEM with 5% FBS before adding experimental reagents. All cell lines were frequently examined using the MycoAlertTM Mycoplasma Detection Kit (Lonza, Verviers, Belgium) to ensure they remained free of mycoplasma contamination.

Tumour and CRC hepatic metastasis mouse xenografts

Four-week-old female BALB/c nude mice were housed under standard conditions. The mice were randomized into two groups, with eight mice per group. HCT116 cells (5×106 cells in 0.1 mL phosphate-buffered saline) transduced with the lentivirus containing BEST4 or EV were injected subcutaneously into the right dorsal flank of mice. Tumour growth was measured twice a week using callipers, and tumour volumes were calculated as length x width2 x 0.5. Mice were sacrificed at 32 days, and tumour weight was measured at the end of the experiment. For further analysis, the excised tumour tissues were divided into two parts and embedded in paraffin or preserved at −80 °C for further analysis.

For the liver metastasis of CRC, intrasplenic injections of HCT-15 cells with BEST4-knockout (BEST4-gRNA), BEST4-rescued or control (EV-gRNA) (5×106 cells in 0.1 mL PBS) were performed into 6-week-old Balb/c nude mice as described previously2. There were 3 mice/group. Briefly, at day 28 after the procedure, mouse livers were paraffin embedded and the sections for H&E staining. The numbers of the metastatic nodules on the livers were double-blind visually quantified and confirmed by a pathologist.

The Animal Ethics Committee approved animal experiments of West China Hospital, Sichuan University (Sichuan, China).

CRC cell lines with overexpression of BEST4

Forced overexpression of BEST4 was examined in HCT116 and Caco2 CRC cells in which the C-terminal HA epitope-tagged human BEST4 gene with GFP (BEST4-HA-GFP) or GFP alone was introduced by lentivirus-mediated gene transfer. Fluorescence-activated cell sorting (FACS) was performed to obtain single cells distributed into 96-well plates. Three independent lines with the highest levels of BEST4 expression were used for subsequent experiments (Figures S1A and S1B). BEST4 mRNA and HA-tagged protein levels were significantly higher in HCT116 and Caco2 cells transfected with BEST4-HA plasmids than those transfected with the empty vector (EV) alone (Figure S1C). The BEST4-overexpressing cell lines were named “HCT116 BEST4-HA” and “Caco2 BEST4-HA.” Cells transfected with the EV alone were referred to as “HCT116 EV” and “Caco2 EV.”

CRISPR/Cas9-mediated knockout of BEST4

BEST4-depleted HCT-15 cells were generated with CRISPR/Cas9 gene-editing technology using a dual sgRNA approach. Two sequences that targeted exon 3 within the BEST4 active fragment (5’-TGACTCTCGTGGTGAACCGC-3’ and 5’-CCGAGATGACGCACATCAGC -3’) were inserted into the pU6-gRNA-Cas9-EGFP vector (GenePharma, Shanghai, China) to generate a CRISPR/Cas9 BEST4 knockout plasmid. Excision of the targeted 44 bp genomic fragment resulted in splicing errors in exons 2 to 4 and generated a premature STOP codon that abrogated functional gene expression (Figures S1F and S1G). Cells were transfected with these plasmids, and GFP+ cells were FACS-sorted as single cells into 96-well plates. After culturing for three weeks, cells were distributed into two 24-well plates, and the appropriate deletion was verified by sequencing. Only cell lines with homozygous deletions were used. Three independent lines generated using this method were used for subsequent experiments and were named “HCT15 BEST4-gRNA.” Diminished expression of immunoreactive BEST4 protein was confirmed by immunoblotting (Figure S1H). The same overexpression strategy was adopted to rescue BEST4 expression in BEST4 knockout HCT-15 cells, named “HCT15 BEST4-Rescued.”

Plasmids and transfection/transduction

Expression plasmids encoding BEST4 (GeneID: 266675, NM_153274; vector: pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro) containing a C-terminal hemagglutinin (HA) epitope tag, HES4 (GeneID: 57801, NM_001142467.2; vector: pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro) containing a N-terminal Flag epitope tag,were synthesized by Public Protein/Plasmid Library (Nanjing, China). According to the manufacturer’s instructions, Lipofectamine 3000 (Invitrogen, Carlsbad, CA, USA) was used in cell transfection experiments.

To generate a model of CRC with forced overexpression of Hes4, cells were transfected with lentiviral pCDH-CMV-MCS-EF1-CopGFP-T2A-Puro vectors containing human Hes4 cDNA and selected with puromycin (Invivogen, San Diego, CA, USA) at 10 µg/mL introduced 48 h after transfection.

For short hairpin RNA (shRNA) and RNA silencing (siRNA) experiments, HEK293 cells were co-transduced with lentiviral vectors carrying shRNA targeting HES4 (Public Protein/Plasmid Library, Nanjing, China; target sequences are listed in Table S1). Supernatants were collected at 48 and 72 h for analysis. Scrambled shRNAs were used to control for non-specific effects. Transduction was performed by mixing aliquots of lentivirus with a standard medium containing 10 μg/mL puromycin (Invivogen) to remove untransduced cells. GeneSolution siRNAs targeting BEST4 (BEST4-siRNA) were used to silence gene expression. Scrambled siRNA (SCR) was used as a control (Qiagen, Hilden, Germany). The target sequences of the BEST4 siRNAs are listed in Table S1. For siRNA experiments, cells were seeded one day before transfection in an antibiotic-free medium and grown to 60% confluency in six-well plates. Cells were transfected using Lipofectamine 3000 as per the manufacturer’s protocol. The efficiency of RNA interference was determined using quantitative polymerase chain reaction (qPCR) and western blotting.

RNA isolation, cDNA library preparation, sequencing, and data analysis

Total RNA was isolated using a High Pure RNA Isolation Kit (Roche, Basel, Switzerland). RNA samples with an RNA integrity number (RIN) ≥7.0 and a 28S:18S ratio ≥ 1.5 were used in subsequent experiments. Sequencing libraries were generated and sequenced by CapitalBio Technology (Beijing, China). A total amount of 3 μg RNA per sample was used. Briefly, the Ribo-Zero™ Magnetic Kit (Epicentre) was used to remove rRNA from the total RNA, and then the NEBNext Ultra RNA Library Prep Kit for Illumina (NEB, USA) was used to construct the libraries for sequencing following the manufacturer’s instructions. The RNA was fragmented into pieces of ∼200 base pairs in length in NEBNext First-Strand Synthesis Reaction Buffer (5X). The first-strand cDNA was synthesized from the RNA fragments using reverse transcriptase and random hexamer primers, and then the second-strand cDNA was synthesized in Second-Strand Synthesis Reaction Buffer with dUTP Mix (10x). The end of the cDNA fragment was subjected to an end-repair process that included the addition of a single “A” base followed by ligation of the adapters. Products were purified and enriched using PCR to amplify the library DNA. The final libraries were qualified using Agilent 2100 and quantified using the KAPA Library Quantification Kit (KAPA Biosystems, South Africa). Finally, the libraries were subjected to paired-end sequencing with a paired-end 150-base pair reading length on an Illumina NovaSeq sequencer (Illumina).

The sequencing quality of raw data in fastq format was assessed using FastQC, and then low-quality data were filtered using the Next Generation Sequencing Quality Control platform. The high-quality clean reads were then aligned to the reference genome using Tophat2 with default parameters. The genome of the human genome version of hg38 (UCSC) was used as the reference. Cufflinks and Cuffmerge software packages were used to assemble the transcripts. All subsequent comparative analyses of lncRNAs and mRNAs were based on the results of the transcripts. Transcripts corresponding to mRNAs or lncRNAs were collected from databases and treated as known lncRNAs and annotated based on information from public databases. The transcripts were treated as novel lncRNAs when their sequence length was >200 and when they were predicted to be non-coding RNAs. Differential expression analyses were performed using the limma package and edgeR. Functional annotation and enrichment analyses were performed using KOBAS 3.0. The target genes of the mRNAs were predicted based on cis- and trans-patterns based on the location on the reference genome and sequence similarity. The raw sequence data reported in this paper were deposited in the NCBI Sequence Read Archive with accession number PRJNA690126.

RNA extraction and real-time PCR

Total RNA was isolated from cell lysates according to the manufacturer’s protocol (Zymo Research, Tustin, CA). A High-Capacity cDNA Reverse Transcription Kit (Thermo Fisher Scientific, Waltham, MA) was used for first-strand cDNA synthesis with 1 µg of total RNA from each sample. The expression of genes and the GAPDH internal control was assayed by qPCR using SYBR Green (Bioline Reagents Ltd, London, UK). Primer sequences are shown in Table S1.

Immunoblotting

Protein extracts were prepared using RIPA lysis buffer (Merck Millipore, Temecula, CA) containing protease inhibitor cocktail and phosphatase inhibitor tablets (Sigma, MO, USA). Protein content was determined using a protein assay kit (Bio-Rad, Hercules, CA). Western blotting was performed as described previously (Wang et al., 2019). All primary (1:1000) and secondary antibodies (1:2000), except BEST4 (1:800; LsBio, Seattle, WA) and anti-Flag M2 (Sigma, MO, USA), were purchased from Cell Signaling Technology (Danvers, MA, USA).

Cell proliferation

Cell proliferation was monitored in real time using an IncuCyte ZOOM live-cell microscope incubator (Essen Bioscience, MI, USA), in which the cell confluence was calculated using IncuCyte software, and the cell proliferation was expressed as the percentage of confluence. According to the manufacturer’s protocol, a Cell Counting KitL8 (CCK-8, Dojindo, Tokyo, Japan) assay was used to confirm cell viability. The absorbance at 450 nm was measured using a microplate reader (BioTek, VT, USA), and growth curves were drawn according to the optical density.

Clonogenesis

A total of 3×103 cells per well were seeded in 6-well plates. The medium was refreshed twice a week. After 2 weeks, colonies were fixed and stained with crystal violet (0.005% in 20% methanol). The numbers of colonies were quantified using GelCount (Oxford Optronix Ltd, Oxford, UK). The assay was carried out in triplicate wells for three independent experiments.

Transwell migration and invasion

Cell migration and invasion assays were performed using Transwell assay with uncoated polycarbonate transwell inserts (Millipore, Billerica MA). Cells were digested and suspended in culture medium without FBS for the migration assay. Cell suspensions were added into the upper chamber of the Transwell insert and then placed into the 24-well plate Transwell containing medium with 10% FBS in the lower chamber. For the invasion assay, the 24-well plate with Transwell inserts was coated with 50 μg/insert of Matrigel matrix on the top of the chamber (BD Biosciences, Oxford, UK). After 48 h, cells that travelled to the lower surface of the insert were stained with crystal violet. Experiments were conducted in triplicate.

Immunohistochemistry

Paraffin-embedded tissue blocks from formalin-fixed tumour samples were sectioned, dewaxed, and rehydrated following standard protocols. Sections were stained for human Ki67 primary antibody (1:200, Cell Signaling Technology, MA, USA), a marker of cell proliferation, and anti-mouse HRP-conjugated secondary antibody (Dako, CA, USA), and the positive cells were counted in eight randomly chosen fields. Expression of BEST4-HA in tumours was stained with anti-HA primary antibody (1:800, Cell Signaling Technology) and anti-rabbit HRP-conjugated secondary antibody (Dako).

Dual-luciferase reporter assay

The BEST4 promoter region (−2000 to +100Lbp) was cloned into pGL3-basic vectors (Promega, WI, USA) to construct the luciferase reporter plasmid (pGL3-BEST4). The stably high Hes4 expression cell line was constructed by infecting HCT116 cells with lentivirus, and then the recombinant plasmid pGL3-BEST4 was co-transfected with the control plasmid pRL-TK (Promega) into HCT116 Hes4 and HCT116 EV cells. Twenty-four hours after transfection, firefly and Renilla luciferase activities were analysed using the dual-luciferase reporter assay (Promega) according to the manufacturer’s instructions, and the results were normalized as relative luciferase activity (firefly luciferase/Renilla luciferase).

Chromatin immunoprecipitation-quantitative PCR (ChIP-qPCR)

ChIP-qPCR was performed as previously described (Miotto and Struhl, 2006). At room temperature, we crosslinked cells at 5×107 cells/mL for 10 min using 1% formaldehyde and stopped the reaction using 125 mM glycine. After three washes with ice-cold PBS, cells were homogenized, lysed, and sonicated to shear DNA into 200–500Lbp fragments. The DNA fragments were incubated with 10Lµg of antibodies against anti-Flag tag (Sigma, MO, USA) or native IgG (Cell Signaling Technology) followed by IP with 60 µl of protein A/G Magnetic Beads (MedChemExpress, New Jersey, USA) and overnight incubation at 4 °C with rotation. Immunoprecipitated DNAs were extracted from the DNA/antibody/protein A/G bead complexes using proteinase K digestion, subjected to reverse crosslinking at 65 °C for 4 h, and purified with spin columns. qPCR analysis was performed to determine the enrichment of DNA fragments using the indicated primers (Table S1). ChIP-qPCR data were normalized using the fold-enrichment method (ChIP signals were divided by IgG signals), and DHFR 5 ’UTR was used as a negative control. Each experiment included triplicate samples and the data shown represent the mean of three independent experiments.

Immunofluorescence staining

HCT116 cells transfected alone or co-transfected with expression vectors encoding C-terminal HA-tagged BEST4, and N-terminal Flag-tagged Hes4 were grown on glass coverslips, fixed for 10 min with 4% paraformaldehyde, permeabilized for 5 min with 0.2% Triton X-100, then blocked for 15 min with 3% bovine serum albumin. HA-tagged BEST4 was stained using an anti-HA antibody (Cell Signaling Technology) followed by a TRITC-labelled secondary antibody (Abcam, Cambridge, UK). Flag-tagged Hes4 was detected using an anti-Flag antibody (Sigma, MO, USA) with an Alexa Fluor 647-labeled secondary antibody (Invitrogen Carlsbad, CA). Cells were mounted and imaged using laser-scanning confocal microscopy (Nikon Corporation, Tokyo, Japan).

Co-immunoprecipitation (Co-IP)

Co-IP assays were performed on nuclear extracts. According to the manufacturer’s protocols, nuclear proteins of each sample were collected using MinuteTM Cytoplasmic and Nuclear Fractionation Kit (Invent, MN, USA). Protein G Dynabeads (Thermo Fisher Scientific, MA, USA) following the manufacturer’s instructions. Briefly, HEK293 cells were co-transfected with expression vectors encoding C-terminal HA-tagged BEST4 and N-terminal Flag-tagged Hes4. Cells were harvested and lysed 48 h after transfection. Cell lysates (500 µg) were incubated overnight at 4 °C in a rotating wheel with 2 µg of anti-FLAG (Sigma, MO, USA) or anti-HA antibody (Cell Signaling Technology) bound to Protein G Dynabeads. Immunocomplexes were separated using a magnet, washed three times in PBS with 0.02% TweenTM 20 and eluted in elution buffer (50 mM glycine pH 2.8). After boiling in sample buffer at 70 °C for 10 min, immunocomplexes were loaded on 4–20% Tris-glycine gels (Bio-Rad, CA, USA), followed by blotting on PVDF membranes and immunoblotting using the indicated antibodies.

Chloride channel efflux

Cells were maintained in a serum free DMEM overnight prior to treatment with DIDS (4,4’-diisothiocyanatostilbene-2,2’-disulfonic acid; HY-D0086, MCE, China), CaCCinh-A01 (HY-100611, MCE, China) or 1 μM ionomycin for 24h as previously published (Liu et al, 2015; Uwada et al, 2019). Chloride channel efflux was evaluated with colorimetric changes by commercially available kits (ab176767, Abcam). Briefly, 40,000 BEST4-expressing or EV-control HCT116 cells were plated per well in a 96-well plate and allowed to grow over night. Before the assay, cells were refreshed with serum-free medium and 100 µL/well of pre-warmed iodide-loading buffer was added and the plate was incubated for 2 hours at 37 L. After washing each well with HBSS three times, cells were lysed and Iodide Sensor Blue dye (50 µL/well) and 0.5 x Iodide Sensor Enhancer (50 µL/well) were added and incubated for 1 minutes before reading at 405 nm. Data was calculated as fold-change relative to control.

Statistical analysis

The results were expressed as the mean ± standard error of the mean. The statistical significance of differences between means was assessed using Student’s unpaired two-tailed t-tests, and the Mann-Whitney U test was performed to compare the variables in two groups using SPSS 25.0 (SPSS, Chicago, USA). The relationship between the clinicopathological parameters of CRC and the expression of BEST4 was examined using the Kruskal-Wallis H test. The Kaplan-Meier method and log-rank tests were used to assess overall survival in relation to BEST4 expression. Differences in cell proliferation and tumour growth rates between the two groups of mice were assessed using repeated-measures analysis of variance. Western blot intensity was assessed using ImageJ v1.53 software (ImageJ, Bethesda, MD, USA). P-values <0.05 indicated statistically significant differences.